Including the 5 year olds as their own age range
also trying to bin the age ranges by age, instad of age range 
also taking the graphs in the Poirel 2011 style (global-local scores)

#libraries and variables
```{r}
library(dplyr)
library(stringr)
library(tidyverse)
library(bbmle)      # for ICtab()
library(readxl)
library("writexl")
library(ggplot2)
library(ggpubr)
library(lme4)       #for glmer
library(car)        # for Anova()
library(emmeans)




left_key = "z"
right_key = "m"

round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}

```
#Colors
This assigns HEX codes for all the colors in the graph
```{r}
angular_color = "#E01A4F"
curved_color = "#FFC05C"
third_color = "#80B8EF"
congruent_color = "#56B375"
incongruent_color = "#9046CF"
```


generating the csvs:
```{r }

correct_stim_list = c("sound/baba_rep.wav" = "bouba",
                      "sound/gaga_rep.wav" = "bouba",
                      "sound/keekee.wav" = "kiki",
                      "sound/teetee.wav" = "kiki")



which_is_correct <- function(stimuli,lefts,rights) {
  
  #Make a new vector the same length as the number of rows
  correct_vec <- rep(NA,length(stimuli))
  
  #For each row in the dataset....
  for(i in seq(1:length(stimuli))){
    
    #Get the correct type ("Bouba" or "Kiki") by checking in the stim list
    correct_type <- correct_stim_list[stimuli[i]]
    
    #If the correct type is in the left one the correct key was the left key
    if(grepl(correct_type, lefts[i], fixed = TRUE)){
      correct_key <- left_key
    }
    #If the correct type is in the right one the correct key was the right key
    else if(grepl(correct_type, rights[i], fixed = TRUE)){
      correct_key <- right_key
    }
    #If it isn't in either something has gone wrong so you'll get an NA
    else{
      correct_key <- NA
    }
    
    #Put that correct key in the output vector
    correct_vec[i] <- correct_key
  }
  
  #Return the final filled in vector
  return(correct_vec)
}

#look at the results files
#this data set in LG_DI_five_rds is NON CONFOUND ONLY- 16 5, 20 6-8, 24 9-11, 41 adults
rds_files <- list.files("LG_DI_five_rds",
                        pattern = "\\.rds$",
                        full.names = TRUE)

rds_files
#change [#] to pick which one to read

for(file in rds_files){
  print(file)
  file_id <- str_extract(file,"b[kl]g\\d\\d\\d")
  
  data <- readRDS(file)
  
  #assign ID
  participant_ID <- data$results$`sp_id`[[1]]
  main_data <- data$results$`Main page`[[1]]
  
  
  df <- read.table(text = main_data, sep =",", header = TRUE, stringsAsFactors = FALSE)
  #df is the raw data, tells you stimulus and responses
  
  
  ##Ben Code ***creating tidy data and choice bias score***
  
  #First remove unneeded columns
  data_cols <- df %>% dplyr::select(c(trial_type,stimulus,response,left_image,right_image,correct_response,correct)) 
  
  #Then Filter practice and experimental trials
  data_prac <- data_cols %>% filter(grepl("Prac", stimulus, fixed = TRUE))
  data_exp <- data_cols %>% filter(!grepl("Prac", stimulus, fixed = TRUE)) %>%
    filter(trial_type  %in% c("bouba-kiki","image-keyboard-response")) %>%
    filter(stimulus != "img/fixation.png")
  
  #filter out BK data 
  data_exp_bk <-data_exp %>% filter(trial_type == "bouba-kiki")
  #filter out the LG data
  data_exp_lg <-data_exp %>% filter(trial_type =="image-keyboard-response") %>%
    dplyr::select(c(trial_type, stimulus, response))
  
  #Now write a function to find if the left or the right image is "correct"
  
  data_exp_bk <- data_exp_bk %>% mutate(correct_response = which_is_correct(stimulus,left_image,right_image))
  data_exp_bk <- data_exp_bk %>% mutate(correct = ifelse(correct_response == response,
                                                         1,
                                                         ifelse(response == left_key | response == right_key,
                                                                0,
                                                                NA)))
  
  data_exp_bk <- data_exp_bk %>% mutate(sound = ifelse(stimulus %in% c("sound/baba_rep.wav","sound/gaga_rep.wav"),
                                                       "round",
                                                       ifelse(stimulus %in% c("sound/teetee.wav","sound/keekee.wav"),
                                                              "spiky",
                                                              NA))) %>%
    filter(!is.na(correct))
  
#adding columns to LG files to do analysis ############
  data_exp_lg <- data_exp_lg %>% separate(stimulus, c("type","image_ID"), sep = "/") 
  
  data_exp_lg <- data_exp_lg %>% group_by(type) %>% 
                                mutate(trial_num = row_number()) %>% 
                                ungroup() %>%
                                pivot_wider(names_from = type, values_from = c(image_ID,response)) %>%
                                dplyr::select(!c(trial_type,response_targets))

  
  
  
  
  file_path_bk <- paste0("LG_DI_five_bk_csv/",file_id,"_bk.csv")
  file_path_lg <- paste0("LG_DI_five_csv/",file_id,"_lg.csv")
  
  #file_path_prac <- paste0("LG practice trials/",file_id,".csv")
  #write.csv(data_prac, file_path_prac)
  
  write.csv(data_exp_bk, file_path_bk) 
  write.csv(data_exp_lg, file_path_lg)
  
}


```


setup putting together the csvs into one dataframe:
```{r}

all_files <- list.files("LG_DI_five_csv")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("lg",all_files[i])){
    print(all_files[i])
    if(first_file){
      LG_data_df <- read.csv(paste0("LG_DI_five_csv/",all_files[i]))
      LG_data_df <- LG_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      LGnew_data_df <- read.csv(paste0("LG_DI_five_csv/",all_files[i]))
      LGnew_data_df <- LGnew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      LG_data_df <- rbind(LG_data_df,LGnew_data_df)
    }
  }
}

#unique(LG_data_df$ID) #at 101 June 5
```

#create bk df
```{r}
all_files <- list.files("LG_DI_five_bk_csv")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("lg",all_files[i])){
    print(all_files[i])
    if(first_file){
      BK_data_df <- read.csv(paste0("LG_DI_five_bk_csv/",all_files[i]))
      BK_data_df <- BK_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      BKnew_data_df <- read.csv(paste0("LG_DI_five_bk_csv/",all_files[i]))
      BKnew_data_df <- BKnew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      BK_data_df <- rbind(BK_data_df,BKnew_data_df)
    }
  }
}

#unique(LG_data_df$ID) #at 101 June 5

#first create a new column shape_choice that has a 1 if they chose round, 0 if they chose spiky
BK_data_df <- BK_data_df %>% mutate(shape_choice = ifelse(grepl("bouba",left_image)  & response == left_key,
                                                         1,
                                                         ifelse(grepl("bouba",right_image)  & response == right_key, 1,
                                                         0))) 
```



#lg create large df
```{r}
#load in the tables of targets and pairs descriptions
target_table <- read_excel("LG_target_table.xlsx")
pairs_table <- read_excel("LG_pair_table.xlsx")
age_table <- read_excel("LG_ages_5.xlsx")
age_table <- age_table %>% mutate(ID = tolower(ID)) #%>% select(ID,Age,Range)

#full_join to combine
LG_data_df_combined <- full_join(LG_data_df,target_table, by="image_ID_targets")
#LG_data_df has no confound image IDs so they are populating as NAs
LG_data_df_combined <- full_join(LG_data_df_combined,pairs_table, by="image_ID_pairs")%>%
  filter(!is.na(ID))
LG_data_df_combined <- full_join(LG_data_df_combined,age_table, by="ID")
#if the the global choice is on the left and they make the "z" response, then put G in the choice column, etc
LG_data_df_combined_bias <- LG_data_df_combined %>% mutate(choice = ifelse(response_pairs == left_key &
                                                                             target_global == pair_left_global,
                                                                           "global", 
                                                                           ifelse(response_pairs == left_key &
                                                                                    target_local == pair_left_local,
                                                                                  "local",
                                                                         ifelse(response_pairs == right_key &
                                                                                  target_global == pair_right_global,
                                                                                "global",
                                                                          ifelse(response_pairs == right_key &
                                                                                    target_local == pair_right_local,
                                                                                  "local",
                                                                                 NA)))))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% filter(!is.na(choice))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% mutate(choice_number = ifelse(choice == "global", 1, 0)) %>%
                            filter(!is.na(choice))

#write.csv(LG_data_df_combined_bias, "significance tables/full data set.csv")
```

#lg How many trials did each participant get?
```{r}
#need to check about the number of trials each participant got
trial_counts <- LG_data_df_combined_bias %>% group_by(ID) %>%
                               summarize(trial_counts = n()) %>%
                                ungroup() %>%
                              summarize(mean = mean(trial_counts),
                                      sd = sd(trial_counts),
                                      se = sd/sqrt(n()))
#23.74257 average

trial_counts_bk <- BK_data_df %>% group_by(ID) %>%
                               summarize(trial_counts = n()) %>%
                                ungroup() %>%
                              summarize(mean = mean(trial_counts),
                                      sd = sd(trial_counts),
                                      se = sd/sqrt(n()))
#31.76238 average
```

new calculation: sum(global)-sum(local)

need to group_by(ID, choice)

```{r}
#creates a count of g - l responses, puts them into categories based on what the end number is (local or global group)
#one row per participant
LG_count <-LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)
LG_count_p <- LG_count %>% pivot_wider(names_from = choice, values_from = n) %>% mutate_all(~replace(., is.na(.), 0))
#new column with local-global
LG_count_p <- LG_count_p %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))

```
adding the local-global value to the LG_data_df_combined_bias

```{r}
LG_poirel_all <- full_join(LG_data_df_combined_bias, LG_count_p, by ="ID")
```

graphing, trying to bin each age, instead of range
change Range to Age
```{r}
#to count choice bias and see how many participants are in each age range
LG_bias_data <- LG_data_df_combined_bias %>% group_by(ID,Range) %>% 
                                    summarise(global_bias = sum(choice_number)/n()) %>% 
                                    group_by(Range) %>%
                                    summarize(mean_bias = mean(global_bias),
                                    sd_bias = sd(global_bias),
                                    se_bias=sd_bias/sqrt(n()),
                                    N=n()) %>% ungroup()

#2 rows for each Range, one local and one global
#instead of LG_poirel_all, try summarizing from an already summarized across participant df
LG_bias_poirel <- LG_poirel_all %>% group_by(ID,Range, LG_group) %>%
                                      summarise(GminusL = mean(GminusL)) %>%
                                    ungroup() %>%
                                    group_by(Range, LG_group) %>%
                                    summarize(mean_bias = mean(GminusL),
                                    sd_bias = sd(GminusL),
                                    n = n(),
                                    se_bias=sd_bias/sqrt(n())) %>% ungroup()




#calculating the points that go on the graph
LG_poirel_points <- LG_poirel_all  %>% group_by(ID,Range, LG_group) %>%
                        mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
                        group_by(Range,bias_round,LG_group) %>%
                        summarise(Count = length(unique(ID)))

#counting number of participants
LG_group_count <- LG_poirel_all %>% group_by(Range, LG_group) %>% summarise(
                                                           count = length(unique(ID)))

#proportion = number in l/g group divided by total N participants in age range #######################

LG_group_count_p <- full_join(LG_group_count, LG_bias_data, by="Range")
LG_group_count_p <- LG_group_count_p %>% mutate(proportion = count/N)


#average values!! average of GminusL for each age range################
LG_weighted_avg <- LG_poirel_all %>% group_by(ID,Range) %>%
                                      summarise(GminusL = mean(GminusL)) %>%
                                    ungroup() %>%
                                    group_by(Range) %>%
                                    summarise(avg_bias = mean(GminusL),
                                              sd_bias = sd(GminusL, na.rm = TRUE),
                                              se_bias=sd_bias/sqrt(n()), 
                                              N = n()) %>% ungroup()

#make one data set with one row for each participant
LG_bias_poirel_one_row <- LG_poirel_all %>% group_by(ID,Range, LG_group) %>%
                                      summarise(GminusL = mean(GminusL))

```

```{r}

####average GminusL for each age range
LG_poirel_plot2 <-ggplot() +
  geom_col(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias), color = "black", fill = NA) +
  geom_col(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias, fill = Range), alpha = 0.5) +
  geom_errorbar(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias, ymin = avg_bias-se_bias,
                                              ymax = avg_bias+se_bias), alpha = 1, width = .75) +
  geom_jitter(LG_bias_poirel_one_row, mapping = aes(x = Range, y = GminusL)) +
  theme_light() +
  ylab("Global Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<- local bias, global bias ->")

LG_poirel_plot2
```
#analysis- are they different from 0? LG_poirel_plot2
```{r}
#LG_bias_poirel_one_row
lgm1 <- glm(GminusL ~ 0 + Range, data = LG_bias_poirel_one_row)
summary(lgm1)
Anova(lgm1)
# none are different from zero


#are they different from each other? no
contrast(emmeans(lgm1, ~ Range) , method = "pairwise", type = "response")

#lg_bias_table <-summary.glm(m1)$coefficients
#write.csv(bko1_bias_table, "significance tables/bko1_bias_table.csv")


#checking 
age_group <- LG_bias_poirel_one_row %>% filter(Range == "5")
# One-sample t-test
res <- t.test(age_group$GminusL, mu = 0)
# Printing the results: significantly different from zero
res 

```

Is there a significant change in the proportion of L to G participants with age?
```{r}
LG_bias_poirel_one_row <- LG_bias_poirel_one_row %>% mutate(LG_group_bi = ifelse(LG_group == "local", 1,0))

lgm1 <- glm(LG_group_bi ~ 0 + Range, data = LG_bias_poirel_one_row, family = binomial)
summary(lgm1)
Anova(lgm1)
```



***************************************************************************
#first half
Testing only the first half of trials for LG
slice only the top 12 rows for each participant
```{r}
#LG_data_df_combined_bias has all trials for each participant
LG_count <-LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)
LG_count_p <- LG_count %>% pivot_wider(names_from = choice, values_from = n) %>% mutate_all(~replace(., is.na(.), 0))
#new column with local-global
LG_count_p <- LG_count_p %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))

#change number in the slice() to change number of trials
LG_half_trials <- LG_data_df_combined_bias %>% group_by(ID) %>%
  dplyr::slice(1:6)
LG_half_trials_bias <- LG_half_trials %>% group_by(ID, Range) %>% count(choice)  %>% 
                        pivot_wider(names_from = choice, values_from = n) %>% 
                        mutate_all(~replace(., is.na(.), 0)) %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))


#now make a df with one row per participant
LG_half_trials_one_row <- LG_half_trials_bias %>% group_by(ID,Range,LG_group) %>%
  summarise(GminusL = mean(GminusL))

#summarizing with the SE and SD
LG_half_trials_graph <- LG_half_trials_bias %>% group_by(Range, LG_group) %>%
  summarize(mean_bias = mean(GminusL),
            sd_bias = sd(GminusL),
            n = n(),
            se_bias=sd_bias/sqrt(n())) %>% ungroup()

#calculating the points that go on the graph
LG_half_trials_points <- LG_half_trials_one_row  %>% group_by(ID,Range, LG_group) %>%
  mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
  group_by(Range,bias_round,LG_group) %>%
  summarise(Count = length(unique(ID)))


```
calculating the average for each age range, instead of splitting it into 2 for LG_group
```{r}
#summarizing with the SE and SD
LG_half_trials_graph_avg <- LG_half_trials_bias %>% group_by(Range) %>%
  summarize(mean_bias = mean(GminusL),
            sd_bias = sd(GminusL),
            n = n(),
            se_bias=sd_bias/sqrt(n())) %>% ungroup()

#calculating the points that go on the graph
LG_half_trials_points_av <- LG_half_trials_one_row  %>% group_by(ID,Range) %>%
  mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
  group_by(Range,bias_round,LG_group) %>%
  summarise(Count = length(unique(ID)))
```


```{r}
#### GminusL for each age range
LG_poirel_plot_half <-ggplot() +
  geom_col(LG_half_trials_graph, mapping = aes(x = interaction(LG_group,Range), y = mean_bias), color = "black", fill = NA) +
  geom_col(LG_half_trials_graph, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, fill = Range), alpha = 0.5) +
  geom_errorbar(LG_half_trials_graph, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, ymin = mean_bias-se_bias,ymax = mean_bias+se_bias), alpha = 1, width = .75) +
  geom_point(LG_half_trials_points, mapping = aes(x = interaction(LG_group,Range), y = bias_round, size = Count, color = Range)) +
  theme_light() +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot_half
```

```{r}
#### GminusL for each age range AVERAGED
LG_poirel_plot_half_av <-ggplot() +
  geom_col(LG_half_trials_graph_avg, mapping = aes(x = Range, y = mean_bias), color = "black", fill = NA) +
  geom_col(LG_half_trials_graph_avg, mapping = aes(x = Range, y = mean_bias, fill = Range), alpha = 0.5) +
  geom_errorbar(LG_half_trials_graph_avg, mapping = aes(x = Range, y = mean_bias, ymin = mean_bias-se_bias,ymax = mean_bias+se_bias), alpha = 1, width = .75) +
  geom_point(LG_half_trials_points_av, mapping = aes(x = Range, y = bias_round, size = Count, color = Range)) +
  theme_light() +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot_half_av
```
analysis how to tell if the age groups are different from each other

```{r}
#by range
lgm_mult <- glm(GminusL ~ Range*LG_group, data = LG_half_trials_one_row)
lgm_add <- glm(GminusL ~ Range+LG_group, data = LG_half_trials_one_row)
ICtab(lgm_mult, lgm_add)

Anova(lgm_add)

contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")
```
analysis how to tell if the averages are different from each other

```{r}
#by range
lgm_mult_b <- aov(GminusL ~ Range, data = LG_half_trials_one_row)

Anova(lgm_mult_b)
summary(lgm_mult_b)
TukeyHSD(lgm_mult_b)

#checking 
five_to_adult <- LG_half_trials_one_row %>%  filter(Range == "5" | Range == "Adult")
# One-sample t-test
res <- t.test(GminusL ~ Range, data = five_to_adult)
res
```

#correlation LG to BK
first make the csvs in LG nc plus bk for all participants- makes 2 files for each person, one _lg and one _bk
```{r}
#look at the results files
rds_files <- list.files("LG_DI_five_rds",
                        pattern = "\\.rds$",
                        full.names = TRUE)

rds_files
#change [#] to pick which one to read

for(file in rds_files){
  print(file)
  file_id <- str_extract(file,"b[kl]g\\d\\d\\d")
  
  data <- readRDS(file)
  
  #assign ID
  participant_ID <- data$results$`sp_id`[[1]]
  main_data <- data$results$`Main page`[[1]]
  
  
  df <- read.table(text = main_data, sep =",", header = TRUE, stringsAsFactors = FALSE)
  #df is the raw data, tells you stimulus and responses
  
  
  ##Ben Code ***creating tidy data and choice bias score***
  
  #First remove unneeded columns
  data_cols <- df %>% select(c(trial_type,stimulus,response,left_image,right_image,correct_response,correct)) 
  
  #Then Filter practice and experimental trials
  data_prac <- data_cols %>% filter(grepl("Prac", stimulus, fixed = TRUE))
  data_exp <- data_cols %>% filter(!grepl("Prac", stimulus, fixed = TRUE)) %>%
    filter(trial_type  %in% c("bouba-kiki","image-keyboard-response")) %>%
    filter(stimulus != "img/fixation.png")
  
  #filter out BK data 
  data_exp_bk <-data_exp %>% filter(trial_type == "bouba-kiki")
  #filter out the LG data
  data_exp_lg <-data_exp %>% filter(trial_type =="image-keyboard-response") %>%
    select(c(trial_type, stimulus, response))
  
  #Now write a function to find if the left or the right image is "correct"
  
  data_exp_bk <- data_exp_bk %>% mutate(correct_response = which_is_correct(stimulus,left_image,right_image))
  data_exp_bk <- data_exp_bk %>% mutate(correct = ifelse(correct_response == response,
                                                         1,
                                                         ifelse(response == left_key | response == right_key,
                                                                0,
                                                                NA)))
  
  data_exp_bk <- data_exp_bk %>% mutate(sound = ifelse(stimulus %in% c("sound/baba_rep.wav","sound/gaga_rep.wav"),
                                                       "round",
                                                       ifelse(stimulus %in% c("sound/teetee.wav","sound/keekee.wav"),
                                                              "spiky",
                                                              NA))) %>%
    filter(!is.na(correct))
  
#adding columns to LG files to do analysis ############
  data_exp_lg <- data_exp_lg %>% separate(stimulus, c("type","image_ID"), sep = "/") 
  
  data_exp_lg <- data_exp_lg %>% group_by(type) %>% 
                                mutate(trial_num = row_number()) %>% 
                                ungroup() %>%
                                pivot_wider(names_from = type, values_from = c(image_ID,response)) %>%
                                select(!c(trial_type,response_targets))

  
  
  
  
  file_path_bk <- paste0("LG nc plus bk/",file_id,"_bk.csv")
  file_path_lg <- paste0("LG nc plus bk/",file_id,"_lg.csv")
  
  #file_path_prac <- paste0("LG practice trials/",file_id,".csv")
  #write.csv(data_prac, file_path_prac)
  
  write.csv(data_exp_bk, file_path_bk) 
  write.csv(data_exp_lg, file_path_lg)
  
}
```

Add them all together
```{r}
all_files <- list.files("LG nc plus bk")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("bk",all_files[i])){
    print(all_files[i])
    if(first_file){
      bk_data_df <- read.csv(paste0("LG nc plus bk/",all_files[i]))
      bk_data_df <- bk_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      bknew_data_df <- read.csv(paste0("LG nc plus bk/",all_files[i]))
      bknew_data_df <- bknew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      bk_data_df <- rbind(bk_data_df,bknew_data_df)
    }
  }
}

unique(bk_data_df$ID)
```
add in ages
```{r}
age_table <- read_excel("LG_ages_5.xlsx")
age_table <- age_table %>% mutate(ID = tolower(ID)) #%>% select(ID,Age,Range)
bk_data_combined <- full_join(bk_data_df,age_table, by="ID")
```
#choice bias calculations
```{r}
#CALCULATE CHOICE BIAS
#first create a new column shape_choice that has a 1 if they chose round, 0 if they chose spiky
bk_data_combined <- bk_data_combined %>% mutate(shape_choice = ifelse(grepl("bouba",left_image)  & response == left_key,
                                                         1,
                                                         ifelse(grepl("bouba",right_image)  & response == right_key, 1,
                                                         0))) 


```
#bk How many trials did each participant get?
```{r}
#need to check about the number of trials each participant got
trial_counts <- bk_data_combined %>% group_by(ID) %>%
                               summarize(trial_counts = n()) %>%
                                ungroup() %>%
                              summarize(mean = mean(trial_counts),
                                      sd = sd(trial_counts),
                                      se = sd/sqrt(n()))
#[1] 31
```

#bk Graph for all the stimuli for all age groups individually
```{r}
bk_bias_data <- bk_data_combined %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,sound,Range) %>% 
                                      summarise(bias = sum(shape_choice)/n() - 0.5) %>% 
                                      group_by(sound,Range) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n()),
                                                N = n()) %>%
                                      ungroup() 

bk_bias_data_points <- bk_data_combined %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,sound,Range) %>% 
                                      summarise(bias = sum(shape_choice)/n() - 0.5) %>% 
                                      ungroup() %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(Range,sound,bias_round) %>%
                                      summarise(Count = n())


```
#GRAPH

```{r}

bk_overall <- ggplot() +
  geom_col(bk_bias_data, mapping = aes(x = sound, y = mean_bias), color = "black", fill = NA) +
  geom_point(bk_bias_data_points, mapping =aes(x = sound, y = bias_round, size = Count, color= sound)) +
  geom_col(bk_bias_data, mapping = aes(x = sound, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_errorbar(bk_bias_data, mapping = aes(x = sound, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  scale_fill_manual(values = c(angular_color,curved_color)) +
  scale_color_manual(values = c(angular_color,curved_color)) +
  theme_light() +
  ylim(-0.5,0.5) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  ylab("Choice Bias") +
  xlab("Stimulus") +
  facet_wrap("Range")

bk_overall
#ggsave("graphs/presentation graphs/bk_overall.png", width = 10, height = 5)
```
#comparing bk choice bias to LG bias
use bias scores (GminusL) from LG poirel with 5 yo.R markdown
is there a correlation between your group (local or global group) and your BK bias score?
```{r}
#make a new dataframe with the following columns for each ID: round/spiky bias scores, GminusL scores, LG_group assignment
LG_score_only <- LG_bias_poirel_one_row %>% dplyr::select(ID, Range, GminusL, LG_group) 

#what should be calculated??? sum correct, or sum shape choice?
BK_bias_only <- bk_data_combined %>% group_by(ID) %>%
                  mutate(total_bk_bias = sum(correct)/n()-.5) %>% dplyr::select(ID, total_bk_bias)  %>%
                filter(row_number()==1)

BK_LG_scores <- full_join(LG_score_only, BK_bias_only, by="ID")

#pearson's correlation 
#make sure the midpoints on each axis is at chance


cor.test(BK_LG_scores$GminusL, BK_LG_scores$total_bk_bias, method = "pearson")
#p-value = 0.6083

cor_plot <-  ggplot(BK_LG_scores, aes(GminusL, total_bk_bias))
cor_plot + geom_point() +
  theme_light()+
  #ylim(-0.50,0.50)+
  geom_smooth(method='lm')+
  facet_wrap("Range")+
  ylab("BK bias in expected direction")+
  xlab("<- local bias, global bias ->")+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))

```


