Before anything else, load in your libraries and check your working directory. The working directory is specific to your computer. 
you need: master demographics log edited.xlsx
          bko2 all trials df.xlsx

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lme4)
library(ggpubr)
library(forcats)
library(bbmle)      # for ICtab()
library(car)        # for Anova()
library(readxl)     #to read excel files

```


First step: load in the demographic data frame. use drop_na() to get rid of NAs in a particular column. In this case we want to get rid of the NAs in Experiment_Run because they were not run in the study.
```{r}
demo_df <- read_excel("master demographics log edited.xlsx")
#Get rid of any rows with NA in them (blank or incomplete data) in the "Experiment Run" column
demo_df <- demo_df %>% drop_na("Experiment_Run")

```

The demographics has too much information in it. We only care about BKO2 data, not any of the other participants. Let's use filter() to pick out exactly the participants we need. We can also use select() to choose columns to include or exclude.
the ! is an important part of R syntax. It means everything but. so != "Exclude" means keep in everything BUT where it says "Exclude". 
```{r}
demo_df_bko2 <- demo_df %>% filter(Experiment_Run =="BKO2")
#filter out some extra participants we don't need. Take out the 2 participants we need to exclude.
demo_df_bko2 <- demo_df_bko2 %>% mutate(Include_Exclude = ifelse(is.na(Include_Exclude), "Include", "Exclude")) %>%   
                                filter(Include_Exclude != "Exclude") %>%
                                mutate(Bilingual = ifelse(Bilingual == "yes",1,0))
```


Now we need to load in the data frame for the bk bias and WJ scores. join them together will fulljoin, which 
uses ID to match them up. 
```{r}
all_data_df <- read_excel("bko2 all trials df.xlsx")
all_data_df <- full_join(all_data_df,demo_df_bko2, by="ID")
```

This dataframe isn't exactly what we need, though. It has lots of trials for each participant. Let's use summarize() to get one number per participant

```{r}
#shape_choice is the proportion of times participants choose a round shape. this is our choice bias measure.
one_row <- all_data_df %>% group_by(ID,Range,Sex,Bilingual,Race) %>%
                              summarise(bias = sum(shape_choice)/n()- 0.5)
```

Let's do some counting. How many participants in each age range fall into the different demo categories?
```{r}
#sum tables
sum_table_sex <- one_row %>% group_by(Range) %>% count(Sex)
sum_table_bilingual <-one_row %>% group_by(Range) %>% count(Bilingual)
sum_table_race <- one_row %>% group_by(Range) %>% count(Race)
sum_table_race_simple <- one_row %>% mutate(Race = ifelse(Race == "White", "White", "nonWhite")) %>%
                          group_by(Range) %>% count(Race)

```

using glm() to see if sex and bilingualism had any effect on bias score and WJ score. glm is a generalized linear model, similar to an anova. It's also referred to as just a regression model. The syntax is a bit complicated, but basically you're seeing if variable 2 (sex) has a significant effect on variable 1 (shape_choice). the shape_choice data is binomial (you either choose round or sharp- 2 choices = binomial). 
Anova runs a type II anova on the model, allowing you to interpret the regression. If the P value for the chi squared test is over .05, it's nonsignificant (which is what we're hoping for here).
```{r}
#sex
glm_sex <- glmer(shape_choice ~ Sex + (1|ID), data = all_data_df, family = "binomial")
Anova(glm_sex)
#p value= 0.8626

#bilingualism
glm_bilingual <- glmer(shape_choice ~ Bilingual + (1|ID), data = all_data_df, family = "binomial")
Anova(glm_bilingual)

#race
#for race analysis, change to either "white" or "nonwhite"
#syntax: ifelse(column == this, replace it with 1, otherwise replace it with 0)
all_data_df_racesimple <- all_data_df %>% mutate(Race = ifelse(Race == "White", "White", "nonWhite"))

glm_race <- glmer(WJ_score ~ Race + (1|ID), data = all_data_df_racesimple, family="poisson")
Anova(glm_race)

```

Same thing for WJ score. Does sex or bilingualism (maybe check race?) have an impact on WJ score?
```{r}
#sex
glm_sex <- glmer(WJ_score ~ Sex + (1|ID), data = all_data_df, family="poisson")
Anova(glm_sex)

#bilingualism
glm_bilingual <- glmer(WJ_score ~ Bilingual + (1|ID), data = all_data_df, family="poisson")
Anova(glm_bilingual)

#race
glm_race <- glmer(WJ_score ~ Race + (1|ID), data = all_data_df_racesimple, family="poisson")
Anova(glm_race)
#race numbers are not even, so not sure if we will report this, too skewed 


```

So far we didn't find any demographic measure had a significant effect on shape choice or WJ score. This means we can collapse across these variables and don't have to take them into account for our larder analyses. 
