First we create the graph of all the 16 stimuli


```{r}
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(forcats)
library(bbmle)      # for ICtab()
library(car)        # for Anova()

```
Colors
```{r}
angular_color = "#E01A4F"
curved_color = "#FFC05C"
third_color = "#80B8EF"
```

```{r}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
```

```{r}
all_files <- list.files("bko2_CSVs")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("b",all_files[i])){
    print(all_files[i])
    if(first_file){
      all_data_df <- read.csv(paste0("bko2_CSVs/",all_files[i]))
      all_data_df <- all_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      new_data_df <- read.csv(paste0("bko2_CSVs/",all_files[i]))
      new_data_df <- new_data_df %>% mutate(ID = substr(all_files[i],1,6))
      all_data_df <- rbind(all_data_df,new_data_df)
    }
  }
}

#filter out the NAs
all_data_df <- all_data_df %>% filter(!is.na(correct))

unique(all_data_df$ID)
left_key = "z"
right_key = "m"
```


```{r}
#CALCULATE CHOICE BIAS
#group_by(ID,sound,group) group for when i have both adults and children
data_orth <- all_data_df %>% group_by(ID,sound) %>%
  summarise(bias = sum(correct)/n())

data_all_sounds <- all_data_df %>% group_by(ID,sound,stimulus) %>%
  summarise(bias = sum(correct)/n())

data_vowel_type <- all_data_df %>% group_by(vowel_type, ID) %>%
  summarise(bias = sum(correct)/n())

data_congruency = all_data_df %>% group_by(congruent, ID) %>%
  summarise(bias = sum(correct)/n())

data_voicing = all_data_df %>% group_by(voicing, ID) %>%
  summarise(bias = sum(correct)/n())

data_consonant = all_data_df %>% group_by(consonant_type, ID) %>%
  summarise(bias = sum(correct)/n())

data_consonant_type = all_data_df_c %>% group_by(consonant_type, ID) %>%
  summarise(bias = sum(sharp_shape_choice)/n())
```

```{r}
#listing comparisons for significance bars
#bias for orthography
orth_comparisons <- list( c("angular", "curved"))

#bias for vowel type
vowel_comparisions <- list( c("/a/", "/i/"))

#bias for congruency
congruency_comparisions <- list( c("congruent", "incongruent"))

#bias for voicing
voicing_comparisions <- list( c("unvoiced", "voiced"))

#bias for consonant type
consonant_comparisons <- list( c("stop", "fricative"),
                        c("fricative", "sonorant"),
                        c("stop", "sonorant"))

```


```{r}
all_data_df <- read.csv("all_data_df.csv")
#this csv file has lala and lili as angular 
```

```{r}
stimulus_bias_data <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,stimulus,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      group_by(stimulus,sound) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) %>%
                                      ungroup() %>%
                                      mutate(stimulus = fct_reorder2(stimulus, sound, mean_bias))

stimulus_bias_data_points <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,stimulus,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      ungroup() %>%
                                      mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(stimulus,sound,bias_round) %>%
                                      summarise(Count = n())
```

ALL STIM GRAPH

```{r}

new_color_all_stim <- ggplot() +
  geom_col(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias), color = "black", fill = NA) +
  geom_point(stimulus_bias_data_points, mapping =aes(x = stimulus, y = bias_round, size = Count, color= sound)) +
  geom_col(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_point(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias)) +
  geom_errorbar(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  scale_fill_manual(values = c(angular_color,curved_color)) +
  scale_color_manual(values = c(angular_color,curved_color)) +
  theme_classic() +
  ylim(-0.5,0.5) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  ylab("Choice Bias") +
  xlab("Stimulus")

new_color_all_stim
#ggsave("graphs/presentation graphs/kids_all_stim.png", width = 10, height = 5)
```
ANALYSIS WITH BONFERONNI CORRECTION 
```{r}
stim_m <- glm(correct ~ 0 + stimulus, data = all_data_df, family = binomial)
summary(stim_m)#$coefficients[,4]



stim_tib <- tibble(categories = row.names(summary(ben_m)$coefficients),
                  old_p = summary(stim_m)$coefficients[,4],
                  p_vals = p.adjust(summary(stim_m)$coefficients[,4], method = "bonferroni", n = 16),
                  p_val_print = sprintf("%.10f", p_vals),
                  sig = ifelse(p_vals<0.05, "significant", "nonsignificant"))
stim_tib

```



orthography graph
```{r}
orth_new <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,sound) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      #mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      group_by(sound) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

orth_new_points <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,sound) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      ungroup() %>%
                                      #mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(sound,bias_round) %>%
                                      summarise(Count = n())

new_orthography <- ggplot(data_orth, aes(x = sound, y = bias)) +
  geom_col(orth_new, mapping = aes(x = sound, y = mean_bias), color = "black", fill = NA) +
  geom_point(orth_new_points, mapping = aes(x = sound, y = bias_round, size = Count, color = sound)) +
  geom_col(orth_new, mapping = aes(x = sound, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_point(orth_new, mapping = aes(x = sound, y = mean_bias)) +
  geom_errorbar(orth_new, mapping = aes(x = sound, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  stat_compare_means(comparisons = orth_comparisons, label.y = c(1.2),
                    label = "p.signif", hide.ns = FALSE) +
  theme_classic() +
  ylim(0, 1.5) +
  scale_fill_manual(values = c(angular_color,curved_color)) +
  scale_color_manual(values = c(angular_color,curved_color)) +
  scale_size_continuous(breaks = c(5, 10, 15)) +
  ylab("Choice Bias") +
  xlab("Sound")

new_orthography

#ggsave("graphs/presentation graphs/sig orthography.png", height = 3.5, width = 3.5)
```
ANALYSIS FOR ORTHOGRAPHY
```{r}
# One-sample t-test
orth <- t.test(bias ~ sound, data = data_orth)
# Printing the results
orth 
```



CONGRUENCY GRAPH

```{r}
congruency_new <- all_data_df %>% group_by(congruent, ID) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      #mutate(bias = ifelse(congruent == "incongruent",-1*bias,bias)) %>%
                                      #ungroup()%>%
                                      group_by(congruent) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

congruency_new_points <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(congruent, ID) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      ungroup() %>%
                                      #mutate(bias = ifelse(congruent == "incongruent",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(congruent,bias_round) %>%
                                      summarise(Count = n())

congruency_plot_new <- ggplot(data_congruency, aes(x = congruent, y = bias)) +
  geom_col(congruency_new, mapping = aes(x = congruent, y = mean_bias), color = "black", fill = NA) +
  geom_point(congruency_new_points, mapping = aes(x = congruent, y = bias_round, size = Count, color = congruent)) +
  geom_col(congruency_new, mapping = aes(x = congruent, y = mean_bias, fill = congruent), alpha = 0.5) +
  geom_point(congruency_new, mapping = aes(x = congruent, y = mean_bias)) +
  geom_errorbar(congruency_new, mapping = aes(x = congruent, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  stat_compare_means(comparisons = congruency_comparisions, label.y = c(1.2),
                    label = "p.signif", hide.ns = TRUE) +
  scale_fill_manual(values = c(angular_color,curved_color)) +
  scale_color_manual(values = c(angular_color,curved_color)) +
  theme_classic() +
  #ylim(-0.5,0.5) +
  ylab("Choice Bias") +
  scale_y_continuous(limits = c(0, 1.5), breaks = c(0.00, 0.25, 0.50, 0.75, 1)) +
  xlab("Congruency")

congruency_plot_new
ggsave("graphs/presentation graphs/congruency_plot_new.png", height = 3.5, width = 3.5)
```
analysis
```{r}
#what is the difference between congruent and incongruent?
# One-sample t-test
con <- t.test(bias ~ congruent, data = data_congruency)
# Printing the results
con 
```



GRAPH FOR VOWEL TYPE
```{r}
vowel_type_mean <- all_data_df %>%  group_by(vowel_type,ID) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      #mutate(bias = ifelse(vowel_type == "/i/",-1*bias,bias)) %>%
                                      group_by(vowel_type) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

vowel_points <- all_data_df %>% group_by(vowel_type,ID) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      ungroup() %>%
                                      #mutate(bias = ifelse(vowel_type == "/i/",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(vowel_type,bias_round) %>%
                                      summarise(Count = n())

vowel_plot <- ggplot(data_vowel_type, aes(x = vowel_type, y = bias)) +
  geom_col(vowel_type_mean, mapping = aes(x = vowel_type, y = mean_bias), color = "black", fill = NA) +
  geom_point(vowel_points, mapping = aes(x = vowel_type, y = bias_round, size = Count, color = vowel_type)) +
  geom_col(vowel_type_mean, mapping = aes(x = vowel_type, y = mean_bias, fill = vowel_type), alpha = 0.5) +
  geom_point(vowel_type_mean, mapping = aes(x = vowel_type, y = mean_bias)) +
  geom_errorbar(vowel_type_mean, mapping = aes(x = vowel_type, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  stat_compare_means(comparisons = vowel_comparisions, label.y = c(1.2),
                    label = "p.signif", hide.ns = TRUE) +
  theme_classic() +
  ylim(0, 1.5) +
  scale_fill_manual(values = c(curved_color,angular_color)) +
  scale_color_manual(values = c(curved_color,angular_color)) +
  scale_size_continuous(breaks = c(5, 10, 15)) +
  ylab("Choice Bias") +
  xlab("Vowel type")

vowel_plot

ggsave("graphs/presentation graphs/vowel plot.png", height = 3.5, width = 3.5)
```
ANALYSIS FOR VOWEL TYPE
```{r}
#what is the difference between /a/ and /i/?
# One-sample t-test
vow <- t.test(bias ~ vowel_type, data = data_vowel_type)
# Printing the results
vow 
```
GRAPH FOR CONSONANT VOICING
```{r}
voicing_mean <- all_data_df %>%  group_by(voicing,ID) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      #mutate(bias = ifelse(voicing == "/i/",-1*bias,bias)) %>%
                                      group_by(voicing) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

voicing_points <- all_data_df %>% group_by(voicing,ID) %>% 
                                      summarise(bias = sum(correct)/n()) %>% 
                                      ungroup() %>%
                                      #mutate(bias = ifelse(voicing == "/i/",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(voicing,bias_round) %>%
                                      summarise(Count = n())

voicing_plot <- ggplot(data_voicing, aes(x = voicing, y = bias)) +
  geom_col(voicing_mean, mapping = aes(x = voicing, y = mean_bias), color = "black", fill = NA) +
  geom_point(voicing_points, mapping = aes(x = voicing, y = bias_round, size = Count, color = voicing)) +
  geom_col(voicing_mean, mapping = aes(x = voicing, y = mean_bias, fill = voicing), alpha = 0.5) +
  geom_point(voicing_mean, mapping = aes(x = voicing, y = mean_bias)) +
  geom_errorbar(voicing_mean, mapping = aes(x = voicing, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  stat_compare_means(comparisons = voicing_comparisions, label.y = c(1.2),
                    label = "p.signif", hide.ns = TRUE) +
  theme_classic() +
  ylim(0, 1.5) +
  scale_fill_manual(values = c(curved_color,angular_color)) +
  scale_color_manual(values = c(curved_color,angular_color)) +
  scale_size_continuous(breaks = c(5, 10, 15)) +
  ylab("Choice Bias") +
  xlab("Consonant voicing")

voicing_plot

#ggsave("graphs/presentation graphs/voicing plot.png", height = 3.5, width = 3.5)
```
ANALYSIS FOR CONSONANT VOICING
```{r}
# One-sample t-test
voi <- t.test(bias ~ voicing, data = data_voicing)
# Printing the results
voi 
```




```{r}
#bias for consonant type
consonant_comparisons <- list( c("stop", "fricative"),
                        c("fricative", "sonorant"),
                        c("stop", "sonorant"))
                        

ggplot(data_consonant, aes(x = consonant_type, y = bias)) +
  geom_boxplot() +
  #  facet_wrap(~ group) +
  stat_summary(fun.y=mean, geom="point", shape=20, size=5, color="black", fill="black") +
  ylim(0,2) +
  theme_light()+
  stat_compare_means(comparisons = consonant_comparisons, label.y = c(1.1, 1.3, 1.5),
                     label = "p.signif", hide.ns = TRUE)
```

I need to know: how often was a round shape chosen when given each of the 3 consonant types?
first add column to all_data_df

```{r}
all_data_df_c <- all_data_df %>% mutate(round_shape_choice = ifelse(grepl("bouba",left_image)  & response == left_key,
                                                         1,
                                                         ifelse(grepl("bouba",right_image)  & response == right_key, 1,
                                                         0))) %>% 
  mutate(sharp_shape_choice = ifelse(grepl("kiki",left_image)  & response == left_key,
                                                         1,
                                                         ifelse(grepl("kiki",right_image)  & response == right_key, 1,
                                                         0)))
```

make consonant graph

```{r}
consonant_graph_df <- all_data_df_c %>% group_by(ID,consonant_type) %>% 
                                      summarise(bias = sum(sharp_shape_choice)/n()) %>% 
                                      #mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      group_by(consonant_type) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

consonant_graph_points <- all_data_df_c %>% group_by(ID,consonant_type) %>% 
                                      summarise(bias = sum(sharp_shape_choice)/n()) %>% 
                                      ungroup() %>%
                                      #mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(consonant_type,bias_round) %>%
                                      summarise(Count = n())

consonant_graph <- ggplot(data_consonant_type, aes(x = consonant_type, y = bias)) +
  geom_col(consonant_graph_df, mapping = aes(x = consonant_type, y = mean_bias), color = "black", fill = NA) +
  geom_point(consonant_graph_points, mapping = aes(x = consonant_type, y = bias_round, size = Count, color = consonant_type)) +
  geom_col(consonant_graph_df, mapping = aes(x = consonant_type, y = mean_bias, fill = consonant_type), alpha = 0.5) +
  geom_point(consonant_graph_df, mapping = aes(x = consonant_type, y = mean_bias)) +
  geom_errorbar(consonant_graph_df, mapping = aes(x = consonant_type, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  theme_classic() +
  ylim(0,1.8) +
  scale_fill_manual(values = c(angular_color,curved_color,third_color)) +
  scale_color_manual(values = c(angular_color,curved_color,third_color)) +
  scale_size_continuous(breaks = c(5, 10, 15)) +
  stat_compare_means(comparisons = consonant_comparisons, label.y = c(1.1, 1.3, 1.5),
                    label = "p.signif", hide.ns = FALSE) +
  ylab("Proportion of sharp shape choices") +
  xlab("consonant type")

consonant_graph

#ggsave("graphs/presentation graphs/consonant_type.png", width = 5, height = 3)
```
ANALYSIS FOR CONSONANT TYPE
```{r}
m_c <- glm(sharp_shape_choice ~ consonant_type, data = all_data_df_c)

Anova(m_c)

contrast(emmeans(m_c, ~ consonant_type) , method = "pairwise", type = "response")

bko2_consonant_table <-contrast(emmeans(m_c, ~ consonant_type) , method = "pairwise", type = "response")

write.csv(bko2_consonant_table, "significance tables/bko2_consonant_table.csv")
```



```{r}
ggplot(data_consonant, aes(x = consonant_type, y = bias)) +
  geom_boxplot() +
  #  facet_wrap(~ group) +
  stat_summary(fun.y=mean, geom="point", shape=20, size=5, color="black", fill="black") +
  ylim(0,2) +
  theme_light()+
  stat_compare_means(comparisons = consonant_comparisons, label.y = c(1.1, 1.3, 1.5),
                     label = "p.signif", hide.ns = TRUE)
```

