calculating bk bias scores for all participants (this is non confound so far)

Colors
```{r}
angular_color = "#E01A4F"
curved_color = "#FFC05C"
```

generating the csvs:
```{r}
library(dplyr)
library(stringr)
library(tidyverse)
library(emmeans)
library(forcats)
library(bbmle)      # for ICtab()
library(car)        # for Anova()


correct_stim_list = c("sound/baba_rep.wav" = "bouba",
                      "sound/gaga_rep.wav" = "bouba",
                      "sound/keekee.wav" = "kiki",
                      "sound/teetee.wav" = "kiki")

left_key = "z"
right_key = "m"
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}

which_is_correct <- function(stimuli,lefts,rights) {
  
  #Make a new vector the same length as the number of rows
  correct_vec <- rep(NA,length(stimuli))
  
  #For each row in the dataset....
  for(i in seq(1:length(stimuli))){
    
    #Get the correct type ("Bouba" or "Kiki") by checking in the stim list
    correct_type <- correct_stim_list[stimuli[i]]
    
    #If the correct type is in the left one the correct key was the left key
    if(grepl(correct_type, lefts[i], fixed = TRUE)){
      correct_key <- left_key
    }
    #If the correct type is in the right one the correct key was the right key
    else if(grepl(correct_type, rights[i], fixed = TRUE)){
      correct_key <- right_key
    }
    #If it isn't in either something has gone wrong so you'll get an NA
    else{
      correct_key <- NA
    }
    
    #Put that correct key in the output vector
    correct_vec[i] <- correct_key
  }
  
  #Return the final filled in vector
  return(correct_vec)
}

#look at the results files
rds_files <- list.files("LG_DI_five_rds",
                        pattern = "\\.rds$",
                        full.names = TRUE)

rds_files
#change [#] to pick which one to read

for(file in rds_files){
  print(file)
  file_id <- str_extract(file,"b[kl]g\\d\\d\\d")
  
  data <- readRDS(file)
  
  #assign ID
  participant_ID <- data$results$`sp_id`[[1]]
  main_data <- data$results$`Main page`[[1]]
  
  
  df <- read.table(text = main_data, sep =",", header = TRUE, stringsAsFactors = FALSE)
  #df is the raw data, tells you stimulus and responses
  
  
  ##Ben Code ***creating tidy data and choice bias score***
  
  #First remove unneeded columns
  data_cols <- df %>% select(c(trial_type,stimulus,response,left_image,right_image,correct_response,correct)) 
  
  #Then Filter practice and experimental trials
  data_prac <- data_cols %>% filter(grepl("Prac", stimulus, fixed = TRUE))
  data_exp <- data_cols %>% filter(!grepl("Prac", stimulus, fixed = TRUE)) %>%
    filter(trial_type  %in% c("bouba-kiki","image-keyboard-response")) %>%
    filter(stimulus != "img/fixation.png")
  
  #filter out BK data 
  data_exp_bk <-data_exp %>% filter(trial_type == "bouba-kiki")
  #filter out the LG data
  data_exp_lg <-data_exp %>% filter(trial_type =="image-keyboard-response") %>%
    select(c(trial_type, stimulus, response))
  
  #Now write a function to find if the left or the right image is "correct"
  
  data_exp_bk <- data_exp_bk %>% mutate(correct_response = which_is_correct(stimulus,left_image,right_image))
  data_exp_bk <- data_exp_bk %>% mutate(correct = ifelse(correct_response == response,
                                                         1,
                                                         ifelse(response == left_key | response == right_key,
                                                                0,
                                                                NA)))
  
  data_exp_bk <- data_exp_bk %>% mutate(sound = ifelse(stimulus %in% c("sound/baba_rep.wav","sound/gaga_rep.wav"),
                                                       "round",
                                                       ifelse(stimulus %in% c("sound/teetee.wav","sound/keekee.wav"),
                                                              "spiky",
                                                              NA))) %>%
    filter(!is.na(correct))
  
#adding columns to LG files to do analysis ############
  data_exp_lg <- data_exp_lg %>% separate(stimulus, c("type","image_ID"), sep = "/") 
  
  data_exp_lg <- data_exp_lg %>% group_by(type) %>% 
                                mutate(trial_num = row_number()) %>% 
                                ungroup() %>%
                                pivot_wider(names_from = type, values_from = c(image_ID,response)) %>%
                                select(!c(trial_type,response_targets))

  
  
  
  
  file_path_bk <- paste0("LG nc plus bk/",file_id,"_bk.csv")
  file_path_lg <- paste0("LG nc plus bk/",file_id,"_lg.csv")
  
  #file_path_prac <- paste0("LG practice trials/",file_id,".csv")
  #write.csv(data_prac, file_path_prac)
  
  write.csv(data_exp_bk, file_path_bk) 
  write.csv(data_exp_lg, file_path_lg)
  
}


```


setup putting together the csvs:
```{r}
library(dplyr)
library(tidyverse)
library(readxl)
library("writexl")
library(ggplot2)
library(ggpubr)
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
left_key = "z"
right_key = "m"

all_files <- list.files("LG nc plus bk")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("bk",all_files[i])){
    print(all_files[i])
    if(first_file){
      bk_data_df <- read.csv(paste0("LG nc plus bk/",all_files[i]))
      bk_data_df <- bk_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      bknew_data_df <- read.csv(paste0("LG nc plus bk/",all_files[i]))
      bknew_data_df <- bknew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      bk_data_df <- rbind(bk_data_df,bknew_data_df)
    }
  }
}

unique(bk_data_df$ID) #at 96 Dec 6

```
add in ages
```{r}
age_table <- read_excel("LG_ages_5.xlsx")
age_table <- age_table %>% mutate(ID = tolower(ID)) #%>% select(ID,Age,Range)
bk_data_combined <- full_join(bk_data_df,age_table, by="ID")
```

calculate bias BK
```{r}
#to count choice bias and see how many participants are in each age range
bk_bias_data <- bk_data_combined %>% group_by(ID,Range,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      mutate(bias = ifelse(sound == "spiky",-1*bias,bias)) %>%
                                      group_by(Range,sound) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n()),
                                                N=n()) %>%
                                      ungroup()

bk_bias_data_points <- bk_data_combined %>% group_by(ID,Range,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      ungroup() %>%
                                      mutate(bias = ifelse(sound == "spiky",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(Range,sound,bias_round) %>%
                                      summarise(Count = n())


```
bk graph attempt
```{r}
bk_range_plot <-ggplot() +
  geom_col(bk_bias_data, mapping = aes(x = sound, y = mean_bias), color = "black", fill = NA) +
  geom_point(bk_bias_data_points, mapping = aes(x = sound, y = bias_round, size = Count, color = sound)) +
  geom_col(bk_bias_data, mapping = aes(x = sound, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_point(bk_bias_data, mapping = aes(x = sound, y = mean_bias)) +
  geom_errorbar(bk_bias_data, mapping = aes(x = sound, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  theme_light() +
  facet_wrap("Range") +
  ylim(-0.5,0.5) +
  ylab("Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  scale_fill_manual(values = c(angular_color,curved_color)) +
  scale_color_manual(values = c(angular_color,curved_color)) +
  xlab("Sound")

bk_range_plot
```

now trying the same thing with each age (each age its own thing)

calculate bias BK
```{r}
#to count choice bias and see how many participants are in each age range
bk_bias_data_age <- bk_data_combined %>% group_by(ID,Age,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      mutate(bias = ifelse(sound == "spiky",-1*bias,bias)) %>%
                                      group_by(Age,sound) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n()),
                                                N=n()) %>%
                                      ungroup()

bk_bias_data_points_age <- bk_data_combined %>% group_by(ID,Age,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      ungroup() %>%
                                      mutate(bias = ifelse(sound == "spiky",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(Age,sound,bias_round) %>%
                                      summarise(Count = n())


```
bk graph attempt
```{r}
bk_range_plot_age <-ggplot() +
  geom_col(bk_bias_data_age, mapping = aes(x = sound, y = mean_bias), color = "black", fill = NA) +
  geom_point(bk_bias_data_points_age, mapping = aes(x = sound, y = bias_round, size = Count, color = sound)) +
  geom_col(bk_bias_data_age, mapping = aes(x = sound, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_point(bk_bias_data_age, mapping = aes(x = sound, y = mean_bias)) +
  geom_errorbar(bk_bias_data_age, mapping = aes(x = sound, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  theme_classic() +
  facet_wrap("Age") +
  ylim(-0.5,0.5) +
  ylab("Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  scale_fill_manual(values = c(angular_color,curved_color)) +
  scale_color_manual(values = c(angular_color,curved_color)) +
  xlab("Sound")

bk_range_plot_age
#ggsave("graphs/binned ages bk.png", width = 6, height = 6)

```

```{r}
#calculating round and spiky bias for each person
bk_data_combined_bias <- bk_data_combined %>% drop_na() %>% 
                  group_by(ID, sound) %>%
                  mutate(bias = sum(correct)/n() - 0.5)

#are they different from 0?
m1 <- glm(bias ~ 0+Range:sound, data = bk_data_combined_bias)
summary(m1)

bko1_bias_table <-summary.glm(m1)$coefficients

#write.csv(bko1_bias_table, "significance tables/bko1_bias_table.csv")


#checking 
age_sound <- bk_data_combined_bias %>% filter(sound == "round") %>% filter(Range == "5")
# One-sample t-test
res <- t.test(age_sound$bias, mu = 0)
# Printing the results: significantly different from zero
res 

#even the 5 year olds are different than 0?? dang
```

how to tell if the age groups are different from each other

```{r}
#by range
m_mult <- glm(bias ~ Range*sound, data = bk_data_combined_bias)
m_add <- glm(bias ~ Range+sound, data = bk_data_combined_bias)
ICtab(m_mult, m_add)

Anova(m_mult)

contrast(emmeans(m_mult, ~ Range | sound) , method = "pairwise", type = "response")
bko1_range_difference_table <-contrast(emmeans(m_mult, ~ Range | sound) , method = "pairwise", type = "response")

#write.csv(bko1_difference_table, "significance tables/bko1_difference_table.csv")

#by age
m_mult_a <- glm(bias ~ Age*sound, data = bk_data_combined_bias)
m_add_a <- glm(bias ~ Age+sound, data = bk_data_combined_bias)
ICtab(m_mult_a, m_add_a)

Anova(m_mult_a)

contrast(emmeans(m_mult_a, ~ Age | sound) , method = "pairwise", type = "response")
bko1_age_difference_table <-contrast(emmeans(m_mult_a, ~ Range | sound) , method = "pairwise", type = "response")
```
Is there a difference in strength overall b/t round and spiky
```{r}

```

comparing bk choice bias to LG bias???
use bias scores (GminusL) from LG poirel with 5 yo.R markdown
is there a correlation between your group (local or global group) and your BK bias score?
```{r}
#make a new dataframe with the following columns for each ID: round/spiky bias scores, GminusL scores, LG_group assignment
LG_score_only <- LG_poirel_all %>% select(ID, Age, Range, GminusL, LG_group) %>% 
                                    group_by(ID) %>% filter(row_number()==1)

BK_bias_only <- bk_data_combined_bias %>% group_by(ID) %>%
                  mutate(total_bk_bias = sum(correct)/n() - 0.5) %>% select(ID, total_bk_bias)  %>%
                filter(row_number()==1)

BK_LG_scores <- full_join(LG_score_only, BK_bias_only, by="ID")

#pearson's correlation 
#make sure the midpoints on each axis is at chance


cor.test(BK_LG_scores$GminusL, BK_LG_scores$total_bk_bias, method = "pearson")
#p-value = 0.6083

cor_plot <-  ggplot(BK_LG_scores, aes(GminusL, total_bk_bias))
cor_plot + geom_point() +
  theme_light()+
  ylim(-0.50,0.50)+
  geom_smooth(method='lm')+
  facet_wrap("Range")+
  ylab("BK bias in expected direction")+
  xlab("<- local bias, global bias ->")
```
Is there any relation between being a local person and your bk bias? 

```{r}
#group BK_LG_scores by LG_group
LG_group_cor_bk <- BK_LG_scores %>% mutate(LG_group_num = ifelse(LG_group == "local", 0,1))

#is there a sig difference between bk_bias in local vs global group 

#does LG_group have an effect on the model of bk_bias?
lgm_lg_bk <- aov(total_bk_bias ~ LG_group_num, data = LG_group_cor_bk)

Anova(lgm_lg_bk)
summary(lgm_lg_bk)

#to see if there is an interaction with range?
lgm_lg_bk_a <- aov(total_bk_bias ~ LG_group_num+Range, data = LG_group_cor_bk)
lgm_lg_bk_m <- aov(total_bk_bias ~ LG_group_num*Range, data = LG_group_cor_bk)
ICtab(lgm_lg_bk_a, lgm_lg_bk_m)

Anova(lgm_lg_bk_a)

contrast(emmeans(lgm_lg_bk_a, ~ Range | LG_group_num) , method = "pairwise", type = "response")


```



