---
title: "final graphs bko1 and bko2"
output: html_document
---
First we create the graph of all the 16 stimuli


```{r}
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(forcats)
library(bbmle)      # for ICtab()
library(car)        # for Anova()

```
Colors
```{r}
angular_color = "#FFA69E"
curved_color = "#B88BBB"
```

```{r}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
```

```{r}
all_data_df <- read.csv("all_data_df.csv")
```

```{r}
stimulus_bias_data <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,stimulus,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      group_by(stimulus,sound) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) %>%
                                      ungroup() %>%
                                      mutate(stimulus = fct_reorder2(stimulus, sound, mean_bias))

stimulus_bias_data_points <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,stimulus,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      ungroup() %>%
                                      mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(stimulus,sound,bias_round) %>%
                                      summarise(Count = n())
```


```{r}
ggplot() +
  geom_col(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias), color = "black", fill = NA) +
  geom_point(stimulus_bias_data_points, mapping = aes(x = stimulus, y = bias_round, size = Count, color = sound)) +
  geom_col(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_point(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias)) +
  geom_errorbar(stimulus_bias_data, mapping = aes(x = stimulus, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  theme_classic() +
  ylim(-0.5,0.5) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  ylab("Bias") +
  xlab("Stimulus")

#ggsave("poster graphs/all_stim_graph.png")
```



load in the bko2 CSV files
all data is all_data_df
```{r}
library(dplyr)
library(bbmle)
library(car)
library(ggpubr)
library(emmeans)


all_files <- list.files("bko2_CSVs")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("b",all_files[i])){
    print(all_files[i])
    if(first_file){
      all_data_df <- read.csv(paste0("bko2_CSVs/",all_files[i]))
      all_data_df <- all_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      new_data_df <- read.csv(paste0("bko2_CSVs/",all_files[i]))
      new_data_df <- new_data_df %>% mutate(ID = substr(all_files[i],1,6))
      all_data_df <- rbind(all_data_df,new_data_df)
    }
  }
}

#filter out the NAs
all_data_df <- all_data_df %>% filter(!is.na(correct))
```

calculate the CHOICE BIAS for each dimension 
```{r}
#CALCULATE CHOICE BIAS
#group_by(ID,sound,group) group for when i have both adults and children
data_orth <- all_data_df %>% group_by(ID,sound) %>%
  summarise(bias = sum(correct)/n())

data_all_sounds <- all_data_df %>% group_by(ID,sound,stimulus) %>%
  summarise(bias = sum(correct)/n())

data_vowel_type <- all_data_df %>% group_by(vowel_type, ID) %>%
  summarise(bias = sum(correct)/n())

data_congruency = all_data_df %>% group_by(congruent, ID) %>%
  summarise(bias = sum(correct)/n())

data_voicing = all_data_df %>% group_by(voicing, ID) %>%
  summarise(bias = sum(correct)/n())
```

calculate means, SE, error bar numbers for each dimension 
```{r}
#calculating means and SE
data_means_orth <- data_orth %>% 
  group_by(sound) %>% # Group the data by sound
  summarize(mean_bias=mean(bias), 
            sd_bias=sd(bias), # Create variable with sd per group
            N_bias=n(), # Create new variable N  per group
            se=sd_bias/sqrt(N_bias), 
            upper_limit=mean_bias+se, # Upper limit
            lower_limit=mean_bias-se) # Lower limit)  

data_means_all <- data_all_sounds %>% 
  group_by(sound, stimulus) %>% # Group the data by sound
  summarize(mean_bias=mean(bias), 
            sd_bias=sd(bias), # Create variable with sd per group
            N_bias=n(), # Create new variable N  per group
            se=sd_bias/sqrt(N_bias), 
            upper_limit=mean_bias+se, # Upper limit
            lower_limit=mean_bias-se) # Lower limit) 

data_means_vowel_type <- data_vowel_type %>%
  group_by(vowel_type) %>% # Group the data by sound
  summarize(mean_bias=mean(bias), 
            sd_bias=sd(bias), # Create variable with sdper group
            N_bias=n(), # Create new variable N of group
            se=sd_bias/sqrt(N_bias), 
            upper_limit=mean_bias+se, # Upper limit
            lower_limit=mean_bias-se) # Lower limit) 

data_means_congruency <- data_congruency %>%
  group_by(congruent) %>% # Group the data by sound
  summarize(mean_bias=mean(bias), 
            sd_bias=sd(bias), # Create variable with sd per group
            N_bias=n(), # Create new variable N  per group
            se=sd_bias/sqrt(N_bias), 
            upper_limit=mean_bias+se, # Upper limit
            lower_limit=mean_bias-se) # Lower limit) 

data_means_voicing <- data_voicing %>%
  group_by(voicing) %>% # Group the data by sound
  summarize(mean_bias=mean(bias), 
            sd_bias=sd(bias), # Create variable with sd  per group
            N_bias=n(), # Create new variable N  per group
            se=sd_bias/sqrt(N_bias), 
            upper_limit=mean_bias+se, # Upper limit
            lower_limit=mean_bias-se) # Lower limit) 
  
```

listing comparisons for significance bars
```{r}
#bias for orthography
orth_comparisons <- list( c("angular", "curved"))

#bias for vowel type
vowel_comparisions <- list( c("/a/", "/i/"))

#bias for congruency
congruency_comparisions <- list( c("congruent", "incongruent"))

#bias for voicing
voicing_comparisions <- list( c("unvoiced", "voiced"))

```

GRAPH TIME WITH SIGNIFICANCE BARS
```{r}
p_orth <- ggplot() + 
  geom_bar(data = data_means_orth,
           aes(x=sound, y=mean_bias, fill = sound), stat="identity", width=0.5) + 
  geom_errorbar(data = data_means_orth, aes(x=sound, ymin=lower_limit, ymax=upper_limit), width=0.40) + 
  geom_count(data = data_orth, aes(x=sound, y=bias)) +
  scale_size_continuous(breaks = c(2, 4, 6, 8, 10, 12, 14)) +
  stat_compare_means(comparisons = orth_comparisons, label.y = c(1),
                     label = "p.signif", hide.ns = FALSE)+
  theme_light()+
  ylim(0,1.2) +
  ylab("choice bias")

p_orth
#ggsave("graphs/orthography new.png", width = 10, height =10)
```
T TEST ORTHOGRAPHY
```{R}
orth_testing_angular <- data_orth %>% filter(sound == "angular")
# One-sample t-test
res <- t.test(orth_testing_angular$bias, mu = 0.5)
# Printing the results
res 
```

```{R}
orth_testing_curved <- data_orth %>% filter(sound == "curved")
# One-sample t-test
res2 <- t.test(orth_testing_curved$bias, mu = 0.5)
# Printing the results
res2 
```

```{R}
p_all <- ggplot() +
  geom_bar(data = data_means_all,
           aes(x=stimulus, y=mean_bias, fill = sound), stat="identity", width=0.5) + 
  geom_errorbar(data = data_means_all, aes(x=stimulus, ymin=lower_limit, ymax=upper_limit), width=0.40) + 
  geom_count(data = data_all_sounds, aes(x=stimulus, y=bias)) +
  scale_size_continuous(breaks = c(2, 4, 6, 8, 10, 12, 14)) +
  theme_light()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylim(0,1.2) +
  ylab("choice bias")

p_all
#ggsave("graphs/all stim.png")

```

```{r}
vowel_comparisions <- list( c("/a/", "/i/"))

stat.test <- compare_means(bias ~ vowel_type, data = data_vowel_type, method = "t.test")

p_vowel <- ggplot(data = data_means_vowel_type, aes(x=vowel_type, y=mean_bias))+
  geom_bar(data = data_means_vowel_type,
          aes(x=vowel_type, y=mean_bias, fill = vowel_type), stat="identity", width=0.5) +
  geom_errorbar(data = data_means_vowel_type, aes(x=vowel_type, ymin=lower_limit, ymax=upper_limit), width=0.40) +
  geom_count(data = data_vowel_type, aes(x=vowel_type, y=bias)) +
  scale_size_continuous(breaks = c(2, 4, 6, 8, 10, 12, 14)) +
  theme_light()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  stat_compare_means(comparisons = vowel_comparisions, label.y = c(1.1),
                    label = "p.signif", hide.ns = TRUE) +
  ylim(0,1.2) +
  ylab("choice bias")

p_vowel
#ggsave("graphs/vowel type.png")

```


```{R}
p_congruency <- ggplot(data = data_congruency, aes(x=congruent, y=bias)) +
  geom_bar(data = data_means_congruency,
           aes(x=congruent, y=mean_bias, fill = congruent), stat="identity", width=0.5) + 
  geom_errorbar(data = data_means_congruency, aes(x=congruent, y = mean_bias, ymin=lower_limit, ymax=upper_limit), width=0.40) + 
  geom_count(data = data_congruency, aes(x=congruent, y=bias)) +
  scale_size_continuous(breaks = c(2, 4, 6, 8, 10, 12, 14)) +
  theme_light()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  stat_compare_means(comparisons = congruency_comparisions, label.y = c(1.1),
                    label = "p.signif", hide.ns = TRUE) +
  ylim(0,1.2) +
  ylab("choice bias strength")

p_congruency
#ggsave("graphs/congruency.png")

```


```{r}

p_voicing <- ggplot(data = data_voicing, aes(x=voicing, y=bias)) +
  geom_bar(data = data_means_voicing,
           aes(x=voicing, y=mean_bias, fill = voicing), stat="identity", width=0.5) + 
  geom_errorbar(data = data_means_voicing, aes(x=voicing, y = mean_bias, ymin=lower_limit, ymax=upper_limit), width=0.40) + 
  geom_count(data = data_voicing, aes(x=voicing, y=bias)) +
  scale_size_continuous(breaks = c(1, 2, 4, 6, 8, 10, 12, 14)) +
  theme_light()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  stat_compare_means(comparisons = voicing_comparisions, label.y = c(1.1),
                    label = "p.signif", hide.ns = TRUE) +
  ylim(0,1.2) +
  ylab("choice bias")

p_voicing
#ggsave("graphs/voicing.png")

```

MODEL GRAPH 
[when l stims are counted as curved correct] there is a sig effect of congruency and 
congruency:vowel type
```{r}
my_comparisons <- list( c("congruent, unvoiced", "incongruent, unvoiced"),
                        c("congruent, voiced", "incongruent, voiced"))
#plotting
model_plot <- ggplot(data_all_biases, aes(x = interaction(congruent,voicing,sep=", "), y = bias, 
                            fill = interaction(congruent,voicing,sep=", ")))+
  geom_boxplot()+
  #geom_boxplot(aes(x = congruent, y = predict(mi_v_c_vt), color = voicing))+
  ylim(0,1.25) +
  facet_wrap(~ vowel_type) +
  scale_fill_manual(values = c(voiced_color,unvoiced_color,
                               "pink","red")) +
  theme_light() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  xlab("Congruency") +
  ylab("Bias") +
  stat_compare_means(comparisons = my_comparisons, label.y = c(1.2,1.1,1.2,1.1),
                     label = "p.signif", hide.ns = TRUE)

model_plot

#ggsave("graphs/model_plot.png")

```

NEW GRAPHS
```{r}
orth_new <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      group_by(sound) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

orth_new_points <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(ID,sound) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      ungroup() %>%
                                      mutate(bias = ifelse(sound == "angular",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(sound,bias_round) %>%
                                      summarise(Count = n())

```
```{r}
new_orthography <- ggplot() +
  geom_col(orth_new, mapping = aes(x = sound, y = mean_bias), color = "black", fill = NA) +
  geom_point(orth_new_points, mapping = aes(x = sound, y = bias_round, size = Count, color = sound)) +
  geom_col(orth_new, mapping = aes(x = sound, y = mean_bias, fill = sound), alpha = 0.5) +
  geom_point(orth_new, mapping = aes(x = sound, y = mean_bias)) +
  geom_errorbar(orth_new, mapping = aes(x = sound, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  theme_classic() +
  ylim(-0.5,0.5) +
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  ylab("Bias") +
  xlab("Sound")

new_orthography

ggsave("graphs/new color scheme/new orthography.png", height = 3.5, width = 5)
```


```{R}
congruency_new <- all_data_df %>% group_by(congruent, ID) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      #mutate(bias = ifelse(congruent == "incongruent",-1*bias,bias)) %>%
                                      #ungroup()%>%
                                      group_by(congruent) %>%
                                      summarize(mean_bias = mean(bias),
                                                sd_bias = sd(bias),
                                                se_bias=sd_bias/sqrt(n())) 

```


```{R}
congruency_new_points <- all_data_df %>% mutate(stimulus = toupper(sub(".wav","",sub("sound/","",stimulus)))) %>%
                                      group_by(congruent, ID) %>% 
                                      summarise(bias = sum(correct)/n() - 0.5) %>% 
                                      ungroup() %>%
                                     # mutate(bias = ifelse(congruent == "incongruent",-1*bias,bias)) %>%
                                      mutate(bias_round = round_any(bias,0.25)) %>%
                                      group_by(congruent,bias_round) %>%
                                      summarise(Count = n())

```
congruency graph
```{r}
congruency_plot <- ggplot(data_congruency, aes(x = congruent, y = bias)) +
  geom_col(congruency_new, mapping = aes(x = congruent, y = mean_bias), color = "black", fill = NA) +
  geom_point(congruency_new_points, mapping = aes(x = congruent, y = bias_round, size = Count, color = congruent)) +
  geom_col(congruency_new, mapping = aes(x = congruent, y = mean_bias, fill = congruent), alpha = 0.5) +
  geom_point(congruency_new, mapping = aes(x = congruent, y = mean_bias)) +
  geom_errorbar(congruency_new, mapping = aes(x = congruent, y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = 0.5) +
  stat_compare_means(comparisons = congruency_comparisions, label.y = c(0.7),
                    label = "p.signif", hide.ns = TRUE) +
  theme_classic() +
  #ylim(0,0.75) +
  ylab("Choice Bias Strength") +
  xlab("Congruency")

congruency_plot
#ggsave("graphs/new color scheme/congruency new plot.png", width = 5, height = 3.5)
```
