Including the 5 year olds as their own age range
also trying to bin the age ranges by age, instad of age range 
also kaing the graphs in the Poirel 2011 style (global-local scores)

generating the csvs:
```{r}
library(dplyr)
library(stringr)
library(tidyverse)

correct_stim_list = c("sound/baba_rep.wav" = "bouba",
                      "sound/gaga_rep.wav" = "bouba",
                      "sound/keekee.wav" = "kiki",
                      "sound/teetee.wav" = "kiki")

left_key = "z"
right_key = "m"

which_is_correct <- function(stimuli,lefts,rights) {
  
  #Make a new vector the same length as the number of rows
  correct_vec <- rep(NA,length(stimuli))
  
  #For each row in the dataset....
  for(i in seq(1:length(stimuli))){
    
    #Get the correct type ("Bouba" or "Kiki") by checking in the stim list
    correct_type <- correct_stim_list[stimuli[i]]
    
    #If the correct type is in the left one the correct key was the left key
    if(grepl(correct_type, lefts[i], fixed = TRUE)){
      correct_key <- left_key
    }
    #If the correct type is in the right one the correct key was the right key
    else if(grepl(correct_type, rights[i], fixed = TRUE)){
      correct_key <- right_key
    }
    #If it isn't in either something has gone wrong so you'll get an NA
    else{
      correct_key <- NA
    }
    
    #Put that correct key in the output vector
    correct_vec[i] <- correct_key
  }
  
  #Return the final filled in vector
  return(correct_vec)
}

#look at the results files
rds_files <- list.files("LG_DI_five_rds",
                        pattern = "\\.rds$",
                        full.names = TRUE)

rds_files
#change [#] to pick which one to read

for(file in rds_files){
  print(file)
  file_id <- str_extract(file,"b[kl]g\\d\\d\\d")
  
  data <- readRDS(file)
  
  #assign ID
  participant_ID <- data$results$`sp_id`[[1]]
  main_data <- data$results$`Main page`[[1]]
  
  
  df <- read.table(text = main_data, sep =",", header = TRUE, stringsAsFactors = FALSE)
  #df is the raw data, tells you stimulus and responses
  
  
  ##Ben Code ***creating tidy data and choice bias score***
  
  #First remove unneeded columns
  data_cols <- df %>% select(c(trial_type,stimulus,response,left_image,right_image,correct_response,correct)) 
  
  #Then Filter practice and experimental trials
  data_prac <- data_cols %>% filter(grepl("Prac", stimulus, fixed = TRUE))
  data_exp <- data_cols %>% filter(!grepl("Prac", stimulus, fixed = TRUE)) %>%
    filter(trial_type  %in% c("bouba-kiki","image-keyboard-response")) %>%
    filter(stimulus != "img/fixation.png")
  
  #filter out BK data 
  data_exp_bk <-data_exp %>% filter(trial_type == "bouba-kiki")
  #filter out the LG data
  data_exp_lg <-data_exp %>% filter(trial_type =="image-keyboard-response") %>%
    select(c(trial_type, stimulus, response))
  
  #Now write a function to find if the left or the right image is "correct"
  
  data_exp_bk <- data_exp_bk %>% mutate(correct_response = which_is_correct(stimulus,left_image,right_image))
  data_exp_bk <- data_exp_bk %>% mutate(correct = ifelse(correct_response == response,
                                                         1,
                                                         ifelse(response == left_key | response == right_key,
                                                                0,
                                                                NA)))
  
  data_exp_bk <- data_exp_bk %>% mutate(sound = ifelse(stimulus %in% c("sound/baba_rep.wav","sound/gaga_rep.wav"),
                                                       "round",
                                                       ifelse(stimulus %in% c("sound/teetee.wav","sound/keekee.wav"),
                                                              "spiky",
                                                              NA))) %>%
    filter(!is.na(correct))
  
#adding columns to LG files to do analysis ############
  data_exp_lg <- data_exp_lg %>% separate(stimulus, c("type","image_ID"), sep = "/") 
  
  data_exp_lg <- data_exp_lg %>% group_by(type) %>% 
                                mutate(trial_num = row_number()) %>% 
                                ungroup() %>%
                                pivot_wider(names_from = type, values_from = c(image_ID,response)) %>%
                                select(!c(trial_type,response_targets))

  
  
  
  
  #file_path_bk <- paste0("LG CSV files Looped/",file_id,"_bk.csv")
  file_path_lg <- paste0("LG_DI_five_csv/",file_id,"_lg.csv")
  
  #file_path_prac <- paste0("LG practice trials/",file_id,".csv")
  #write.csv(data_prac, file_path_prac)
  
  #write.csv(data_exp_bk, file_path_bk) 
  write.csv(data_exp_lg, file_path_lg)
  
}


```


setup putting together the csvs:
```{r}
library(dplyr)
library(tidyverse)
library(readxl)
library("writexl")
library(ggplot2)
library(ggpubr)
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
left_key = "z"
right_key = "m"

all_files <- list.files("LG_DI_five_csv")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("lg",all_files[i])){
    print(all_files[i])
    if(first_file){
      LG_data_df <- read.csv(paste0("LG_DI_five_csv/",all_files[i]))
      LG_data_df <- LG_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      LGnew_data_df <- read.csv(paste0("LG_DI_five_csv/",all_files[i]))
      LGnew_data_df <- LGnew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      LG_data_df <- rbind(LG_data_df,LGnew_data_df)
    }
  }
}

unique(LG_data_df$ID) #at 94 oct 25
```

```{r}
#load in the tables of targets and pairs descriptions
target_table <- read_excel("LG_target_table.xlsx")
pairs_table <- read_excel("LG_pair_table.xlsx")
age_table <- read_excel("LG_ages_5.xlsx")
age_table <- age_table %>% mutate(ID = tolower(ID)) #%>% select(ID,Age,Range)

#full_join to combine
LG_data_df_combined <- full_join(LG_data_df,target_table, by="image_ID_targets")
#LG_data_df has no confound image IDs so they are populating as NAs
LG_data_df_combined <- full_join(LG_data_df_combined,pairs_table, by="image_ID_pairs")%>%
  filter(!is.na(ID))
LG_data_df_combined <- full_join(LG_data_df_combined,age_table, by="ID")
#if the the global choice is on the left and they make the "z" response, then put G in the choice column, etc
LG_data_df_combined_bias <- LG_data_df_combined %>% mutate(choice = ifelse(response_pairs == left_key &
                                                                             target_global == pair_left_global,
                                                                           "global", 
                                                                           ifelse(response_pairs == left_key &
                                                                                    target_local == pair_left_local,
                                                                                  "local",
                                                                         ifelse(response_pairs == right_key &
                                                                                  target_global == pair_right_global,
                                                                                "global",
                                                                          ifelse(response_pairs == right_key &
                                                                                    target_local == pair_right_local,
                                                                                  "local",
                                                                                 NA)))))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% filter(!is.na(choice))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% mutate(choice_number = ifelse(choice == "global", 1, 0)) %>%
                            filter(!is.na(choice))
```

new calculation: sum(global)-sum(local)

need to group_by(ID, choice)

```{r}
LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)

LG_count <-LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)
LG_count_p <- LG_count %>% pivot_wider(names_from = choice, values_from = n) %>% mutate_all(~replace(., is.na(.), 0))
#new column with local-global
LG_count_p <- LG_count_p %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))

```
adding the local-global value to the LG_data_df_combined_bias

```{r}
LG_poirel_all <- full_join(LG_data_df_combined_bias, LG_count_p, by ="ID")
```

graphing, trying to bin each age, instead of range
```{r}
#to count choice bias and see how many participants are in each age range
LG_bias_data <- LG_data_df_combined_bias %>% group_by(ID,Age) %>% 
                                    summarise(global_bias = sum(choice_number)/n()) %>% 
                                    group_by(Age) %>%
                                    summarize(mean_bias = mean(global_bias),
                                    sd_bias = sd(global_bias),
                                    se_bias=sd_bias/sqrt(n()),
                                    N=n()) %>% ungroup()

#2 rows for each ID- local group and global group
LG_bias_poirel <- LG_poirel_all %>% group_by(Age, LG_group) %>%
                                    summarize(mean_bias = mean(GminusL),
                                              #is this making it too small because it's divided by group?
                                    sd_bias = sd(GminusL),
                                    n = n(),
                                    se_bias=sd_bias/sqrt(n())) %>% ungroup()

LG_poirel_points <- LG_poirel_all  %>% group_by(ID,Age, LG_group) %>%
                        mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
                        group_by(Age,bias_round,LG_group) %>%
                        summarise(Count = length(unique(ID)))



#GRAPH TIME
LG_poirel_plot <-ggplot() +
  geom_col(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Age), y = mean_bias), color = "black", fill = NA) +
  geom_point(LG_poirel_points, mapping = aes(x = interaction(LG_group,Age), y = bias_round, size = Count, color = Age)) +
  geom_col(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Age), y = mean_bias, fill = Age), alpha = 0.5) +
  geom_point(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Age), y = mean_bias)) +
  geom_errorbar(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Age), y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  theme_classic() +
  #facet_wrap("Range") +
  ylab("Global Bias") +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot
```
analysis- are they different from 0?
```{r}
#LG_poirel_all
lgm1 <- glm(GminusL ~ 0+Age:LG_group, data = LG_poirel_all)
summary(lgm1)

#double check- but I'm pretty sure this means they're all different from zero

#lg_bias_table <-summary.glm(m1)$coefficients
#write.csv(bko1_bias_table, "significance tables/bko1_bias_table.csv")


#checking 
age_group <- LG_poirel_all %>% filter(LG_group == "local") %>% filter(Range == "5")
# One-sample t-test
res <- t.test(age_group$GminusL, mu = 0)
# Printing the results: significantly different from zero
res 

```

how to tell if the age groups are different from each other

```{r}
#by range
lgm_mult <- glm(GminusL ~ Range*LG_group, data = LG_poirel_all)
lgm_add <- glm(GminusL ~ Range+LG_group, data = LG_poirel_all)
ICtab(lgm_mult, lgm_add)

Anova(lgm_mult)

contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")
bko1_range_difference_table <-contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")

#write.csv(bko1_difference_table, "significance tables/bko1_difference_table.csv")

#by age
lgm_mult_a <- glm(bias ~ Age*LG_group, data = LG_poirel_all)
lgm_add_a <- glm(bias ~ Age+LG_group, data = LG_poirel_all)
ICtab(lgm_mult_a, lgm_add_a)

Anova(lgm_mult_a)

contrast(emmeans(lgm_mult_a, ~ Age | LG_group) , method = "pairwise", type = "response")
#bko1_age_difference_table <-contrast(emmeans(lgm_mult_a, ~ Age | LG_group) , method = "pairwise", type = "response")
```

