Including the 5 year olds as their own age range
also trying to bin the age ranges by age, instad of age range 
also taking the graphs in the Poirel 2011 style (global-local scores)

#libraries and variables
```{r}
library(dplyr)
library(stringr)
library(tidyverse)
library(bbmle)      # for ICtab()
library(readxl)
library("writexl")
library(ggplot2)
library(ggpubr)
library(lme4)       #for glmer



left_key = "z"
right_key = "m"

round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}

```



setup putting together the csvs into one dataframe:
```{r}

all_files <- list.files("LG_DI_five_csv")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe
for(i in 1:length(all_files)){
  if(grepl("lg",all_files[i])){
    print(all_files[i])
    if(first_file){
      LG_data_df <- read.csv(paste0("LG_DI_five_csv/",all_files[i]))
      LG_data_df <- LG_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      LGnew_data_df <- read.csv(paste0("LG_DI_five_csv/",all_files[i]))
      LGnew_data_df <- LGnew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      LG_data_df <- rbind(LG_data_df,LGnew_data_df)
    }
  }
}

unique(LG_data_df$ID) #at 101 June 5
```

#create large df
```{r}
#load in the tables of targets and pairs descriptions
target_table <- read_excel("LG_target_table.xlsx")
pairs_table <- read_excel("LG_pair_table.xlsx")
age_table <- read_excel("LG_ages_5.xlsx")
age_table <- age_table %>% mutate(ID = tolower(ID)) #%>% select(ID,Age,Range)

#full_join to combine
LG_data_df_combined <- full_join(LG_data_df,target_table, by="image_ID_targets")
#LG_data_df has no confound image IDs so they are populating as NAs
LG_data_df_combined <- full_join(LG_data_df_combined,pairs_table, by="image_ID_pairs")%>%
  filter(!is.na(ID))
LG_data_df_combined <- full_join(LG_data_df_combined,age_table, by="ID")
#if the the global choice is on the left and they make the "z" response, then put G in the choice column, etc
LG_data_df_combined_bias <- LG_data_df_combined %>% mutate(choice = ifelse(response_pairs == left_key &
                                                                             target_global == pair_left_global,
                                                                           "global", 
                                                                           ifelse(response_pairs == left_key &
                                                                                    target_local == pair_left_local,
                                                                                  "local",
                                                                         ifelse(response_pairs == right_key &
                                                                                  target_global == pair_right_global,
                                                                                "global",
                                                                          ifelse(response_pairs == right_key &
                                                                                    target_local == pair_right_local,
                                                                                  "local",
                                                                                 NA)))))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% filter(!is.na(choice))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% mutate(choice_number = ifelse(choice == "global", 1, 0)) %>%
                            filter(!is.na(choice))

#write.csv(LG_data_df_combined_bias, "significance tables/full data set.csv")
```

#How many trials did each participant get?
```{r}
#need to check about the number of trials each participant got
trial_counts <- LG_data_df_combined_bias %>% group_by(ID) %>%
                               summarize(trial_counts = n()) %>%
                                ungroup() %>%
                              summarize(mean = mean(trial_counts),
                                      sd = sd(trial_counts),
                                      se = sd/sqrt(n()))
#23.74257 average
```

new calculation: sum(global)-sum(local)

need to group_by(ID, choice)

```{r}
LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)

LG_count <-LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)
LG_count_p <- LG_count %>% pivot_wider(names_from = choice, values_from = n) %>% mutate_all(~replace(., is.na(.), 0))
#new column with local-global
LG_count_p <- LG_count_p %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))

```
adding the local-global value to the LG_data_df_combined_bias

```{r}
LG_poirel_all <- full_join(LG_data_df_combined_bias, LG_count_p, by ="ID")
```

graphing, trying to bin each age, instead of range
change Range to Age
```{r}
#to count choice bias and see how many participants are in each age range
LG_bias_data <- LG_data_df_combined_bias %>% group_by(ID,Range) %>% 
                                    summarise(global_bias = sum(choice_number)/n()) %>% 
                                    group_by(Range) %>%
                                    summarize(mean_bias = mean(global_bias),
                                    sd_bias = sd(global_bias),
                                    se_bias=sd_bias/sqrt(n()),
                                    N=n()) %>% ungroup()

#2 rows for each Range, one local and one global
#instead of LG_poirel_all, try summarizing from an already summarized across participant df
LG_bias_poirel <- LG_poirel_all %>% group_by(ID,Range, LG_group) %>%
                                      summarise(GminusL = mean(GminusL)) %>%
                                    ungroup() %>%
                                    group_by(Range, LG_group) %>%
                                    summarize(mean_bias = mean(GminusL),
                                    sd_bias = sd(GminusL),
                                    n = n(),
                                    se_bias=sd_bias/sqrt(n())) %>% ungroup()

LG_bias_poirel_one_row <- LG_poirel_all %>% group_by(ID,Range, LG_group) %>%
                                      summarise(GminusL = mean(GminusL))




#calculating the points that go on the graph
LG_poirel_points <- LG_poirel_all  %>% group_by(ID,Range, LG_group) %>%
                        mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
                        group_by(Range,bias_round,LG_group) %>%
                        summarise(Count = length(unique(ID)))

#counting number of participants
LG_group_count <- LG_poirel_all %>% group_by(Range, LG_group) %>% summarise(
                                                           count = length(unique(ID)))

LG_group_count_p <- full_join(LG_group_count, LG_bias_data, by="Range")
#proportion = number in l/g group divided by total N participants in age range #######################
LG_group_count_p <- LG_group_count_p %>% mutate(proportion = count/N)


#average values!! average of GminusL for each age range################
LG_weighted_avg <- LG_poirel_all %>% group_by(ID,Range) %>%
                                      summarise(GminusL = mean(GminusL)) %>%
                                    ungroup() %>%
                                    group_by(Range) %>%
                                    summarise(avg_bias = mean(GminusL),
                                              sd_bias = sd(GminusL, na.rm = TRUE),
                                              se_bias=sd_bias/sqrt(n()), 
                                              N = n()) %>% ungroup()

#make one data set with one row for each participant
LG_average_gminusl <- LG_poirel_all %>% group_by(ID,Range) %>%
                                      summarise(GminusL = mean(GminusL))

```

```{r}

#GRAPH TIME
LG_poirel_plot <-ggplot() +
  geom_col(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias), color = "black", fill = NA) +
  geom_point(LG_poirel_points, mapping = aes(x = interaction(LG_group,Range), y = bias_round, size = Count, color = Range)) +
  geom_col(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, fill = Range), alpha = 0.5) +
  geom_point(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias)) +
  geom_errorbar(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1, width = .75) +
  theme_classic() +
  #facet_wrap("Range") +
  ylab("Global Bias") +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot
```

```{r}

####average GminusL for each age range
LG_poirel_plot2 <-ggplot() +
  geom_col(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias), color = "black", fill = NA) +
  geom_col(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias, fill = Range), alpha = 0.5) +
  geom_errorbar(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias, ymin = avg_bias-se_bias,
                                              ymax = avg_bias+se_bias), alpha = 1, width = .75) +
  geom_jitter(LG_bias_poirel_one_row, mapping = aes(x = Range, y = GminusL)) +
  theme_light() +
  ylab("Global Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot2
```
analysis- are they different from 0? LG_poirel_plot
```{r}
#LG_bias_poirel_one_row
stim_o <- glmer(shape_choice ~ 0 + sound:Range + (1|ID), data = all_data_df, family = binomial)
summary(stim_o)

lgm1 <- glm(GminusL ~ 0+Range:LG_group, data = LG_bias_poirel_one_row)
summary(lgm1)

# they're all different from zero

#lg_bias_table <-summary.glm(m1)$coefficients
#write.csv(bko1_bias_table, "significance tables/bko1_bias_table.csv")


#checking 
age_group <- LG_bias_poirel_one_row %>% filter(LG_group == "local") %>% filter(Range == "5")
# One-sample t-test
res <- t.test(age_group$GminusL, mu = 0)
# Printing the results: significantly different from zero
res 

```

how to tell if the age groups are different from each other

```{r}
library(car)        # for Anova()
library(ggpubr)
library(emmeans)


#by range
lgm_mult <- glm(GminusL ~ Range*LG_group, data = LG_bias_poirel_one_row)
lgm_add <- glm(GminusL ~ Range+LG_group, data = LG_bias_poirel_one_row)
ICtab(lgm_mult, lgm_add)

Anova(lgm_mult)

contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")
bko1_range_difference_table <-contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")

#write.csv(bko1_difference_table, "significance tables/bko1_difference_table.csv")

#by age
lgm_mult_a <- glm(bias ~ Age*LG_group, data = LG_bias_poirel_one_row)
lgm_add_a <- glm(bias ~ Age+LG_group, data = LG_bias_poirel_one_row)
ICtab(lgm_mult_a, lgm_add_a)

Anova(lgm_mult_a)

contrast(emmeans(lgm_mult_a, ~ Age | LG_group) , method = "pairwise", type = "response")
#bko1_age_difference_table <-contrast(emmeans(lgm_mult_a, ~ Age | LG_group) , method = "pairwise", type = "response")
```

weighted ave plot: how to tell if the age groups are different from each other

```{r}
library(car)        # for Anova()
library(ggpubr)
library(emmeans)


#by range
lgm_mult_b <- aov(GminusL ~ Range, data = LG_average_gminusl)

#### are the weighted averages different from each other? LG_average_gminusl dataset 
Anova(lgm_mult_b)
summary(lgm_mult_b)
TukeyHSD(lgm_mult_b)

contrast(emmeans(lgm_mult_b, ~ Range | LG_group) , method = "pairwise", type = "response")
bko1_range_difference_table <-contrast(emmeans(lgm_mult_b, ~ Range | LG_group) , method = "pairwise", type = "response")

#write.csv(bko1_difference_table, "significance tables/bko1_difference_table.csv")

```

***************************************************************************
Testing only the first half of trials for LG
slice only the top 12 rows for each participant
```{r}
#LG_data_df_combined_bias has all trials for each participant


LG_count <-view(LG_data_df_combined_bias) %>% group_by(ID) %>% count(choice)
LG_count_p <- LG_count %>% pivot_wider(names_from = choice, values_from = n) %>% mutate_all(~replace(., is.na(.), 0))
#new column with local-global
LG_count_p <- LG_count_p %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))

#change number in the slice() to change number of trials
LG_second_half_trials <- LG_data_df_combined_bias %>% group_by(ID) %>%
  dplyr::slice(13:24)
LG_second_half_trials <- LG_second_half_trials %>% group_by(ID, Range) %>% count(choice)  %>% 
                        pivot_wider(names_from = choice, values_from = n) %>% 
                        mutate_all(~replace(., is.na(.), 0)) %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local")) %>% mutate(half = "Second")

#change number in the slice() to change number of trials
LG_first_half_trials <- LG_data_df_combined_bias %>% group_by(ID) %>%
  dplyr::slice(1:12)
LG_first_half_trials <- LG_first_half_trials %>% group_by(ID, Range) %>% count(choice)  %>% 
                        pivot_wider(names_from = choice, values_from = n) %>% 
                        mutate_all(~replace(., is.na(.), 0)) %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local")) %>% mutate(half = "First")

LG_both_halves <- rbind(LG_first_half_trials, LG_second_half_trials)

half_m <- glm(GminusL ~ half*Range, data = LG_both_halves)
Anova(half_m)










#now make a df with one row per participant
LG_second_half_trials_one_row <- LG_second_half_trials_bias %>% group_by(ID,Range,LG_group) %>%
  summarise(GminusL = mean(GminusL))

LG_second_half_trials_one_row_edited <- LG_second_half_trials_one_row %>% mutate(GminusL_second = GminusL) 

#summarizing with the SE and SD
LG_second_half_trials_graph <- LG_second_half_trials_bias %>% group_by(Range, LG_group) %>%
  summarize(mean_bias = mean(GminusL),
            sd_bias = sd(GminusL),
            n = n(),
            se_bias=sd_bias/sqrt(n())) %>% ungroup()

#calculating the points that go on the graph
LG_half_trials_points <- LG_half_trials_one_row  %>% group_by(ID,Range, LG_group) %>%
  mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
  group_by(Range,bias_round,LG_group) %>%
  summarise(Count = length(unique(ID)))

#is there a difference in the gminusL scores for first half vs second half? need one df


```
calculating the average for each age range, instead of splitting it into 2 for LG_group
```{r}
#summarizing with the SE and SD
LG_half_trials_graph_avg <- LG_half_trials_bias %>% group_by(Range) %>%
  summarize(mean_bias = mean(GminusL),
            sd_bias = sd(GminusL),
            n = n(),
            se_bias=sd_bias/sqrt(n())) %>% ungroup()

#calculating the points that go on the graph
LG_half_trials_points_av <- LG_half_trials_one_row  %>% group_by(ID,Range) %>%
  mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
  group_by(Range,bias_round,LG_group) %>%
  summarise(Count = length(unique(ID)))
```


```{r}
#### GminusL for each age range
LG_poirel_plot_half <-ggplot() +
  geom_col(LG_half_trials_graph, mapping = aes(x = interaction(LG_group,Range), y = mean_bias), color = "black", fill = NA) +
  geom_col(LG_half_trials_graph, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, fill = Range), alpha = 0.5) +
  geom_errorbar(LG_half_trials_graph, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, ymin = mean_bias-se_bias,ymax = mean_bias+se_bias), alpha = 1, width = .75) +
  geom_point(LG_half_trials_points, mapping = aes(x = interaction(LG_group,Range), y = bias_round, size = Count, color = Range)) +
  theme_light() +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot_half
```

```{r}
#### GminusL for each age range AVERAGED
LG_poirel_plot_half_av <-ggplot() +
  geom_col(LG_half_trials_graph_avg, mapping = aes(x = Range, y = mean_bias), color = "black", fill = NA) +
  geom_col(LG_half_trials_graph_avg, mapping = aes(x = Range, y = mean_bias, fill = Range), alpha = 0.5) +
  geom_errorbar(LG_half_trials_graph_avg, mapping = aes(x = Range, y = mean_bias, ymin = mean_bias-sd_bias,ymax = mean_bias+sd_bias), alpha = 1, width = .75) +
  geom_point(LG_half_trials_points_av, mapping = aes(x = Range, y = bias_round, size = Count, color = Range)) +
  theme_light() +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot_half_av
```
analysis how to tell if the age groups are different from each other

```{r}
#by range
lgm_mult <- glm(GminusL ~ Range*LG_group, data = LG_half_trials_one_row)
lgm_add <- glm(GminusL ~ Range+LG_group, data = LG_half_trials_one_row)
ICtab(lgm_mult, lgm_add)

Anova(lgm_add)

contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")
bko1_range_difference_table <-contrast(emmeans(lgm_mult, ~ Range | LG_group) , method = "pairwise", type = "response")
```
analysis how to tell if the averages are different form each other

```{r}
#by range
lgm_mult_b <- aov(GminusL ~ Range, data = LG_half_trials_one_row)

Anova(lgm_mult_b)
summary(lgm_mult_b)
TukeyHSD(lgm_mult_b)

#checking 
five_to_adult <- LG_half_trials_one_row %>%  filter(Range == "5" | Range == "Adult")
# One-sample t-test
res <- t.test(GminusL ~ Range, data = five_to_adult)
res
```

