Wanted to try making a new way to graph things. see LG Bias Calculation for the normal 
scale of global bias score as a proportion value

This is based off of Poire 2011, where they calculated global-local and plotted positive and negative values 
so with 24 trials, a -24 means all local and +24 means all global 


setup:
```{r}
library(dplyr)
library(tidyverse)
library(readxl)
library("writexl")
library(ggplot2)
library(ggpubr)
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
left_key = "z"
right_key = "m"

all_files <- list.files("LG tidy csv")
first_file <- TRUE

#Adds ID code onto each trial, binds all individual csvs into one large dataframe with all trials for all participants
for(i in 1:length(all_files)){
  if(grepl("b",all_files[i])){
    print(all_files[i])
    if(first_file){
      LG_data_df <- read.csv(paste0("LG tidy csv/",all_files[i]))
      LG_data_df <- LG_data_df %>% mutate(ID = substr(all_files[i],1,6))
      first_file <- FALSE
    }
    else{
      LGnew_data_df <- read.csv(paste0("LG tidy csv/",all_files[i]))
      LGnew_data_df <- LGnew_data_df %>% mutate(ID = substr(all_files[i],1,6))
      LG_data_df <- rbind(LG_data_df,LGnew_data_df)
    }
  }
}
```


```{r}
#load in the tables of targets and pairs descriptions
target_table <- read_excel("LG_target_table.xlsx")
pairs_table <- read_excel("LG_pair_table.xlsx")
age_table <- read_excel("LG_ages.xlsx")
age_table <- age_table %>% mutate(ID = tolower(ID)) #%>% select(ID,Age,Range)

#full_join to combine
LG_data_df_combined <- full_join(LG_data_df,target_table, by="image_ID_targets")
#LG_data_df has no confound image IDs so they are populating as NAs
LG_data_df_combined <- full_join(LG_data_df_combined,pairs_table, by="image_ID_pairs")%>%
  filter(!is.na(ID))
LG_data_df_combined <- full_join(LG_data_df_combined,age_table, by="ID")
#if the the global choice is on the left and they make the "z" response, then put G in the choice column, etc
LG_data_df_combined_bias <- LG_data_df_combined %>% mutate(choice = ifelse(response_pairs == left_key &
                                                                             target_global == pair_left_global,
                                                                           "global", 
                                                                           ifelse(response_pairs == left_key &
                                                                                    target_local == pair_left_local,
                                                                                  "local",
                                                                         ifelse(response_pairs == right_key &
                                                                                  target_global == pair_right_global,
                                                                                "global",
                                                                          ifelse(response_pairs == right_key &
                                                                                    target_local == pair_right_local,
                                                                                  "local",
                                                                                 NA)))))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% filter(!is.na(choice))
LG_data_df_combined_bias <- LG_data_df_combined_bias %>% mutate(choice_number = ifelse(choice == "global", 1, 0)) %>%
                            filter(!is.na(choice))
```

new calculation: sum(global)-sum(local)

```{r}
LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)

LG_count <-LG_data_df_combined_bias %>% group_by(ID) %>% count(choice)
LG_count_p <- LG_count %>% pivot_wider(names_from = choice, values_from = n) %>% mutate_all(~replace(., is.na(.), 0))
#new column with local-global
LG_count_p <- LG_count_p %>% mutate(GminusL = global-local) %>% mutate(LG_group = ifelse(GminusL >0, "global", "local"))

```
adding the local-global value to the LG_data_df_combined_bias

```{r}
LG_poirel_all <- full_join(LG_data_df_combined_bias, LG_count_p, by ="ID")
```

calculating things for graphing
```{r}
#to count choice bias and see how many participants are in each age range
LG_bias_data <- LG_data_df_combined_bias %>% group_by(ID,Range) %>% 
                                    summarise(global_bias = sum(choice_number)/n()) %>% 
                                    group_by(Range) %>%
                                    summarize(mean_bias = mean(global_bias),
                                    sd_bias = sd(global_bias),
                                    se_bias=sd_bias/sqrt(n()),
                                    N=n()) %>% ungroup()

#2 rows for each ID- local group and global group
LG_bias_poirel <- LG_poirel_all %>% group_by(Range, LG_group) %>%
                                    summarize(mean_bias = mean(GminusL),
                                #is this making it too small because it's divided by group? it's dividing by number of trials, not participants
                                    sd_bias = sd(GminusL),
                                    se_bias=sd_bias/sqrt(n())) %>% ungroup()
#in past analysis, N was number of trials (double check, stats ppl says that's incorrect) 

#calculating the points that go on the graph
LG_poirel_points <- LG_poirel_all  %>% group_by(ID,Range, LG_group) %>%
                        mutate(bias_round = round_any(GminusL,5)) %>%  ungroup() %>%
                        group_by(Range,bias_round,LG_group) %>%
                        summarise(Count = length(unique(ID)))


#counting number of participants
LG_group_count <- LG_poirel_all %>% group_by(Range, LG_group) %>% summarise(
                                                           count = length(unique(ID)))
LG_group_count_p <- full_join(LG_group_count, LG_bias_data, by="Range")
#proportion = number in l/g group divided by total N participants in age range #######################
LG_group_count_p <- LG_group_count_p %>% mutate(proportion = count/N)


#average values!! average of GminusL for each age range################
LG_weighted_avg <- LG_poirel_all %>% group_by(Range) %>%
                                    summarise(avg_bias = mean(GminusL),
                                              sd_bias = sd(avg_bias),
                                              se_bias=sd_bias/sqrt(n()), 
                                              N = n()) %>% ungroup()

```

```{r}
#GRAPH TIME
LG_poirel_plot <-ggplot() +
  geom_col(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias), color = "black", fill = NA) +
  geom_point(LG_poirel_points, mapping = aes(x = interaction(LG_group,Range), y = bias_round, size = Count, color = Range)) +
  geom_col(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, fill = Range), alpha = 0.5) +
  geom_point(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias)) +
  geom_errorbar(LG_bias_poirel, mapping = aes(x = interaction(LG_group,Range), y = mean_bias, ymin = mean_bias-se_bias, ymax = mean_bias+se_bias), alpha = 1) +
  theme_classic() +
  ylab("Global Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot

#average GminusL for each age range
LG_poirel_plot2 <-ggplot() +
  geom_col(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias), color = "black", fill = NA) +
  geom_col(LG_weighted_avg, mapping = aes(x = Range, y = avg_bias, fill = Range), alpha = 0.5) +
  theme_light() +
  ylab("Global Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("global and local groups in each age range") +
  ylab("<local bias, global bias>")

LG_poirel_plot2
```
count plot?
```{r}
#LG_group_count need to calculate the proportion, not a count
#is there an increase in local or global group assignment as a function of age?


p <- ggplot(LG_group_count_p, aes(interaction(LG_group,Range), proportion))
p + geom_point() +
  theme_light()


```
age as a point plot? point plot, but I don't think this is very useful at all 
```{r}
LG_poirel_plot3 <-ggplot() +
  geom_point(LG_poirel_all, mapping = aes(x = Age, y = GminusL), color = "black", fill = NA) +

  theme_light() +
  ylab("Global Bias") +
  #scale_color_manual(values = rev(cols)) +
  #scale_fill_manual(values = rev(cols)) +
  xlab("Age") +
  ylab("<local bias, global bias>")

LG_poirel_plot3
```



